---
title: "DifferentialExpressionAnalysis_PTB_TBM"
author: "Triet"
date: "2024-01-18"
output: html_document
---

# Hey! I am trying to organize all the work

## 1. Import libraries and data

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE)
library(parallel)
mcore<-1 # for Window PC

#Load libraries
library(dplyr)
library(plyr)
library(readxl)
library(writexl)
library(survival)
library(glmnet)
library(stabs)
library(tidyverse)
library(magrittr)
library(Hmisc)
library(gtsummary)
library(WGCNA)
library(ggcorrplot)
library(scales)
library(gridExtra)
library(ggcorrplot)
library(broom)
library(rms)
library(tidyverse)
library(stabs)
library(mboost)
library(DESeq2)
library(CEMiTool)
library(igraph)
```

```{r}
path_output<-paste0(str_replace_all(Sys.getenv("USERPROFILE"), '\\\\', '/'),
                     "/OneDrive - Oxford University Clinical Research Unit/#OUCRU-TB/#oucru-tb/PTB_project/Triet_Results")
path_input <- paste0(str_replace_all(Sys.getenv("USERPROFILE"), '\\\\', '/'),
                     "/OneDrive - Oxford University Clinical Research Unit/#OUCRU-TB/#oucru-tb/PTB_project/")
load(paste0(path_input,"/Raw_data/vst_Gensymbol_allPTB_295Sample_18Feb22.RData")) #vst_data 295 31425
load(paste0(path_input,"/Raw_data/vst_Gensymbol_allTBM_281Sample_12Jan24.RData")) #tbm_vst 281 31381
rownames(tbm_vst) <- tbm_vst$LIMS_ID
load(paste0(path_input,"/Data/Fluidigm_PTB_data.Rdata"))
load(paste0(path_input,"/Data/Most_variance_RNA_genes.Rdata"))
load(file=paste0(path_input,"Raw_data/count_data_adjusted_ComBat.Rdata"))
load(paste0(path_input, "Raw_data/Data_RNAseq_RUN1andRUN2_15Feb2023.RData"))
All_sample_RNAseq <- readxl::read_excel(paste0(path_input,"Raw_data/All_sample_RNAseq.xlsx"),
                                        sheet = "Run1and2") %>% as.data.frame()
rownames(All_sample_RNAseq) <- All_sample_RNAseq$LIMS_ID

load(file=paste0(path_input,"Raw_data/Data_26_27_CT_CNIH4.Rdata.RData"))
Fludigm_CNIH4_PTB <- get(load(paste0(path_input,'Raw_data/Fludigm_CNIH4_PTB.Rdata')))

ModuleHubgeneCT <- read.csv(paste0(path_input,"Data/Modules-Hubgenes_CT_value.csv"))
load(file=paste0(path_input,"Data/Gene Significance and Module Membership_clinical_trait.Rdata"))
load(file = paste0(path_input,"Data/PTB-01-dataInput.RData"))
load(file = paste0(path_input,"Data/PTB-02-networkConstruction-auto.RData"))
load(file = paste0(path_input,"Data/Module_discovery.Rdata"))
load(file=paste0(path_input,"Raw_data/PTB_TOM_10000-block.1.RData"))
TOM1 <- as.matrix(TOM)
colnames(TOM1) <- colnames(multiExpr[[1]]$data)
rownames(TOM1) <- colnames(multiExpr[[1]]$data)

clinical_2_discovery <- filter(clinical_2,cohort=='Discovery')
rownames(clinical_2_discovery) <- clinical_2_discovery$LIMS_ID
```

```{r}
vst_ptb_tbm <- rbind.fill(vst_data,tbm_vst)
vst_ptb_tbm %<>% mutate(Type=ifelse(LIMS_ID %in% vst_data$LIMS_ID,"PTB","TBM"))

healthy_ComBat <- count_data_adjusted_ComBat %>% filter(LIMS_ID %in% filter(Cli_All,trial_number %in% c('HV','43TB'))$LIMS_ID)
qt<-quantile(healthy_ComBat$CNIH4,c(0.75)) #Q3 CNIH4 of healthy control

PTB_TBM_ComBat <- count_data_adjusted_ComBat %>% filter(LIMS_ID %in% filter(Cli_All,(Timepoint=='D0') & (trial_number %in% c('MDR_PTB','DS_PTB','26TB','27TB')))$LIMS_ID)
PTB_TBM_ComBat %<>% mutate(CNIH4level=ifelse((CNIH4<qt[1]),1,2))

vst_ptb_tbm <- merge(vst_ptb_tbm,PTB_TBM_ComBat %>% select('LIMS_ID','CNIH4level'),by="LIMS_ID")
rownames(vst_ptb_tbm) <- vst_ptb_tbm$LIMS_ID
```

## 2. Helper functions

```{r}
posterior_predict_hurdle_gaussian <- function(i, prep, ...) {
  mu <- brms::get_dpar(prep, "mu", i = i)
  sigma <- brms::get_dpar(prep, "sigma", i = i)
  theta <- brms::get_dpar(prep, "hu", i = i)
     
  hu <- runif(prep$ndraws, 0, 1)
  ifelse(hu < theta, 0, rnorm(prep$ndraws, mu,sigma))
}
   
posterior_epred_hurdle_gaussian <- function(prep) {
  with(prep$dpars, mu * (1 - hu))
}

cor.pval.test <- function(x1, x2, ...) {
  r <- ncol(x1)
  n <- ncol(x2)
  p.mat<- matrix(NA, r, n)
  for (i in 1:r) {
    for (j in 1:n) {
      tmp <- cor.test(x1[, i], x2[, j], ...)
      p.mat[i, j] <- tmp$p.value
    }
  }
  rownames(p.mat) <-  colnames(x1)
  colnames(p.mat) <- colnames(x2)
  return(p.mat)
}

anno_gene_symbol <- function(data,data_anno,export, name=NULL){
  anno_DESeq2 <- data_anno[,c("gene_id", "gene_symbol")]
  anno_DESeq2 <- subset(anno_DESeq2, gene_id %in% data$gene_id)
  data
  return(data)
}

get_genelist_pathway_kegg <- function(hsa_ID){
  library("KEGGREST")
  names <- keggGet(hsa_ID)[[1]]$GENE
  namesodd <-  names[seq(0,length(names),2)]
  namestrue <- gsub("\\;.*","",namesodd)
}

draw_colnames_45 <- function (coln, gaps, ...) {
    coord <- pheatmap:::find_coordinates(length(coln), gaps)
    x     <-  coord$coord - 0.5 * coord$size
    res   <- grid::textGrob(
      coln, x = x, y = unit(1, "npc") - unit(3,"bigpts"),
      vjust = 0.75, hjust = 1, rot = 45, gp = grid::gpar(...)
    )
    return(res)
}

assignInNamespace(
  x = "draw_colnames",
  value = "draw_colnames_45",
  ns = asNamespace("pheatmap")
)

# Modify ordering of the clusters using clustering callback option
callback <- function(hc, mat){
    sv = svd(t(mat))$v[,1]
    dend = reorder(as.dendrogram(hc), wts = sv)
    as.hclust(dend)
}

make_face_names <- function(mat, rc_fun, rc_names_b = NA, 
                            rc_names_i = NA) {
  f_names <- rc_fun(mat)
  ids_b <- rc_names_b %>% match(rc_fun(mat))
  ids_i <- rc_names_i %>% match(rc_fun(mat))
  
  ids_b %>%
    walk(
      function(i)
        f_names[i] <<-
        bquote(bold(.(rc_fun(mat)[i]))) %>%
        as.expression()
    )
  ids_i %>%
    walk(
      function(i)
        f_names[i] <<-
        bquote(italic(.(rc_fun(mat)[i]))) %>%
        as.expression()
    )
  
  f_names
}

color.bar <- function(lut, min, max=-min, nticks=11, ticks=seq(min, max, len=nticks), title='') {
  scale = (length(lut)-1)/(max-min)
  plot(c(0,10), c(min,max), type='n', bty='n', xaxt='n', xlab='', yaxt='n', ylab='', main=title)
  axis(2, ticks, las=1)
  for (i in 1:(length(lut)-1)) {
    print(lut[i])
    y = (i-1)/scale + min
    rect(0,y,10,y+1/scale, col=lut[i], border=NA)
  }
}

```

## \*Draft analysis - Playground (just for the experimental stuffs)

```{r}
#load(file="Data/Module_discovery.Rdata")
## Module-trait association analysis
sizeGrWindow(10,6)
textMatrix<-list()
xLabels = c("Gene-Xpert \n Ct value", "Cavity","Lung proportion\n damage")

# png(file=paste0(path_output_2,"/Figure 1A-ModuleTraitRelationships-PTB.png"),
#     wi = 8, he = 8,units = 'in', res = 550)
par(mfrow = c(1,2),mar = c(5,6,2.5,1))
nSets = 2
set = 1
# datTraits<-traitData[[set]]$data %>% dplyr::select(c("log2_CT", "Cavity", "Lung_proportion"))
# Will display correlations and their p-values
textMatrix[[set]] =  paste(signif(moduleTraitCor[[set]][module_order,c("log2_CT", "Cavity", "Lung_proportion")], 2), "\n(",
                    signif(moduleTraitPvalue[[set]][module_order,c("log2_CT", "Cavity", "Lung_proportion")], 1), ")", sep = "");
dim(textMatrix[[set]]) = dim(moduleTraitCor[[set]][module_order,c("log2_CT", "Cavity", "Lung_proportion")])
# png(file=paste0(path_output_2,"/Figure 1A-ModuleTraitRelationships-PTB_",shortLabels[set],".png"),
#     units="px", width=1800, height=1800, res=300)
# par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor.scaled[[set]][module_order,c("log2_CT", "Cavity", "Lung_proportion")],
               xLabels = xLabels,
               yLabels = module_order,
               ySymbols = module_order,
               colorLabels = FALSE,
               colors = blueWhiteRed(50),
               textMatrix = textMatrix[[set]],
               setStdMargins = FALSE,
               cex.text = 0.7,
               zlim = c(-3,3),
               main = paste0(shortLabels[set]," cohort"))


```

```{r}
library(ggdendro)
# Set up variables to contain the ME
MEs = list();
varExplained_firstPC <- list()
nSets <- 2
# Calculate the ME for discovery and validation
for (set in 1:nSets){
  temp_ME <- as.data.frame(moduleEigengenes(multiExpr[[set]]$data, moduleColors)$eigengenes)
  temp_ME_order <- orderMEs(temp_ME)
  MEs[[set]] = list(data = temp_ME_order)
  temp_PC <- as.data.frame(moduleEigengenes(multiExpr[[set]]$data, moduleColors)$varExplained)
  names(temp_PC)<-colnames(temp_ME)
  varExplained_firstPC[[set]] = list(data = temp_PC)
}
# re-order the names of module colors validation cohort as the same in the discovery cohorts
MEs[[2]]$data = MEs[[2]]$data[,names(MEs[[1]]$data)]
# Remove all "ME" from the names of MEs
colnames(MEs[[1]]$data)<-gsub("ME","",colnames(MEs[[1]]$data))
colnames(MEs[[2]]$data)<-gsub("ME","",colnames(MEs[[2]]$data))

ME_dat<-MEs[[1]]$data
cor_mat <- cor(ME_dat,use='pairwise.complete.obs',method = "spearman")
dist_matrix <- as.dist(1-cor_mat)
hc <- hclust(dist_matrix, method="ward.D2")
module_order<-rev(hc$labels[hc$order])
ME_dat<-ME_dat[,module_order]
cor_method="spearman"
mat2 <- cor(ME_dat,use='pairwise.complete.obs', method = cor_method)
p.mat2 <- cor.pval.test(ME_dat, ME_dat,method=cor_method, use='pairwise.complete.obs')


# p1<-ggdendrogram(hc, rotate =T, theme_dendro = TRUE,size = 3)+
#   ylab("")+xlab("") +
#   theme_void()+ 
#   theme(legend.position="bottom")+
#   theme(panel.grid.minor = element_blank(),axis.title.x = element_blank(),
#         axis.title.y = element_text(face="bold", colour="black", size=12),
#         axis.text.y = element_text(face="bold",colour="black", size=13),
#         axis.text.x = element_blank(),
#         axis.ticks.x=element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text( colour="black", size=12),
#         legend.key = element_rect(colour = NA),
#         strip.text=element_text(face = "bold",size=12)) + 
#   theme(plot.title = element_text(hjust = 0.5,face="bold", colour="black", size=20))
# col=c("#001164", 'white', "#FF681E")
# 
# p2 <-ggcorrplot(mat2,
#                p.mat = p.mat2, 
#                colors = col,
#                hc.order = FALSE,
#                type = 'full',
#                outline.color = 'black',lab = T, lab_size = 3,insig="blank",
#                show.diag = T) +
#     scale_fill_gradient2(low=col[1], mid= col[2], high=col[3], na.value = 'gray50', limits=c(-1,1))+
#     labs(fill="Corr")+
#     theme(axis.text.x = element_blank(),axis.text.y = element_text(face="bold", colour="black", size=12),legend.text = element_text(size = 15),
#         legend.title = element_text( colour="black", size=12))+theme(legend.position="right")

module_discovery <- signif(moduleTraitCor[[1]][module_order,c("log2_CT")], 2) %>% as.data.frame()
module_discovery<-module_discovery[match(rownames(mat2), rownames(module_discovery)),]

p.discovery <- signif(moduleTraitPvalue[[1]][module_order,c("log2_CT")], 1) %>% as.data.frame()
p.discovery<- p.discovery[match(rownames(mat2), rownames(p.discovery)),]

module_validation <- signif(moduleTraitCor[[2]][module_order,c("log2_CT")], 2) %>% as.data.frame()
module_validation<-module_validation[match(rownames(mat2), rownames(module_validation)),]

p.validation <- signif(moduleTraitPvalue[[2]][module_order,c("log2_CT")], 1) %>% as.data.frame()
p.validation<- p.validation[match(rownames(mat2), rownames(p.validation)),]

module_all <- c(module_discovery,module_validation)
module_all

```

```{r}

library(igraph)
library(qgraph)
# Keep only high correlations
mat <- mat2
mat[p.mat2>=0.05] <- 0
mat[mat<0.5&mat>-0.5] <- mat[mat<0.5&mat>-0.5]/15

sig1 <- symnum(p.discovery, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("*** ", " **", " *", "  .", "     "))
sig2 <- symnum(p.validation, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("  ***", "** ", "* ", ".  ", "     "))
sig <- data.frame(sig1 = sig1, sig2 = sig2) %>% within(newsig <- paste(sig1,sig2, sep=" "))
sig<- sig$newsig

#colors <- colorRampPalette(c("#0091ff", "#f0650e"))(100)[cut(module_all, breaks = seq(-1.6, 1.6, len = 100),include.lowest = TRUE)]

colors <-blueWhiteRed(100,gamma = 0.4)[cut(module_all, breaks = seq(-1.6, 1.6, len = 100),include.lowest = TRUE)]

colors_discovery <- data.frame(module = colnames(ME_dat),
                               color = colors[1:18],
                               levels = module_discovery)

colors_validation <- data.frame(module = colnames(ME_dat),
                               color = colors[19:36],
                               levels = module_validation)




colors <- data.frame(module = colnames(ME_dat),
                     color = colors,#natparks.pals("Arches",n=18),
                     levels = c(module_discovery,module_validation))
colors1 <- filter(colors,levels%in%module_discovery)
colors2 <- filter(colors,levels%in%module_validation)
colors1 <- colors1$color[match(module_discovery, colors1$levels)] #order by module
colors2 <- colors2$color[match(module_validation, colors2$levels)] #order by module
colors = list()
for(i in 1:18){
  colors[[i]] = c(colors1[i],colors2[i])
}
colors1
# colors <- data.frame(color = colorRampPalette(c("#4477AA","#BB4444"))(36),#natparks.pals("Arches",n=18),
#                       levels = sort(c(tmp1,tmp2)))
# 
# colors1 <- filter(colors,levels%in%tmp1)
# colors2 <- filter(colors,levels%in%tmp2)
# colors1 <- colors1$color[match(tmp1, colors1$levels)] #order by module
# colors2 <- colors2$color[match(tmp2, colors2$levels)] #order by module
# colors = list()
# for(i in 1:18){
#   colors[[i]] = c(colors1[i],colors2[i])
# }

network <- graph_from_adjacency_matrix(mat, weighted=T, mode="undirected", diag=F)
#E(network)$weight <- abs(E(network)$weight)
tab <- table(moduleColors) %>% as.data.frame
node.size <- tab[match(rownames(mat), tab$moduleColors),]$Freq
node.colors <- c("cyan","#8A553A","#A38DC9","pink","turquoise","#FDFD96","#2E91E5","grey","grey60","tan","#ff5148","#44D044","lightcyan","black","midnightblue","#e5097f","#FFA07A","greenyellow")
node.label.size <- c(0.4,0.55,0.65,0.65,0.65,0.65,0.65,0.65,0.65,0.65,0.5,0.5,0.65,0.65,0.65,0.65,0.65,0.65)


e <- get.edgelist(network,names=FALSE)
l <- qgraph.layout.fruchtermanreingold(e,
                                       vcount=vcount(network),
                                       area=8*(vcount(network)^2),
                                       repulse.rad=(vcount(network)^3.1)
                                       )

#png(file=paste0(path_output,"/Figure_correlation_network.png"),res=900, units = 'in', width=6.5, height = 6.5)

#layout(matrix(c(1,2), nrow=1), widths=c(3,1))
plot(network,
     layout= l,
     vertex.label="",
     vertex.size=log2(node.size)*3.5,
     #vertex.size=node.size*0.02,
     vertex.color=node.colors,
     # vertex.label.color = ifelse(rownames(mat)%in%c('blue','brown'),  'white','black'),
     # vertex.label.dist=ifelse(rownames(mat)%in%c('blue','brown','turquoise'), 0, 1),
     # vertex.label.degree = ifelse(rownames(mat)%in%c('blue','brown','turquoise'), 0, 92),
     edge.color = adjustcolor(c("#FF681E", "#001164")[(E(network)$weight<0)+1], 0.7),
     edge.width=abs((E(network)$weight))*5,
     edge.curved=0.0001,
     )

plot(network,
     layout= l,
     vertex.label=sig,
     vertex.label.cex=node.label.size,
     vertex.size=log2(node.size)*3.5/1.7, 
     vertex.label.dist = 0.01,
     edge.color=NA,
     vertex.label.degree=0,
     vertex.label.color='yellow',
     add=T,
     vertex.shape="pie",
     vertex.pie=list(c(10,10)),
     vertex.pie.color=colors,
     vertex.label.degree=0.0,
     margin=c(0,0,0,0),
     )

#color.bar(blueWhiteRed(100,gamma = 0.4) , -1.6, 1.6)
#dev.off()
#
png(file=paste0(path_output,"/Figure_tmp.png"),res=900, units = 'in', width=7.5, height = 7.5)



network <- graph_from_adjacency_matrix(mat, weighted=T, mode="directed", diag=F)
e <- get.edgelist(network,names=FALSE)
l <- qgraph.layout.fruchtermanreingold(e,
                                       vcount=vcount(network),
                                       )

plot(network,vertex.shape="pie",
     layout=l,
     vertex.label="",edge.arrow.mode=0,
     vertex.pie=list(c(10,10)),
     #vertex.size=log2(node.size)*3.5,
     vertex.pie.color=colors,
     #edge.color = adjustcolor(c("#FF681E", "#001164")[(E(network)$weight<0)+1], 0.7),
     #edge.width=abs((E(network)$weight))*5,
     )



set.seed(2)
plot(network,
     vertex.label=NA,
     vertex.size=log2(node.size)*3.5/1.7,
     vertex.color=node.colors,
     edge.color=NA,
     add=TRUE)
dev.off()
```

```{r}
library(igraph)
library(ggraph)
library(tidygraph)
library(qgraph)
library(scatterpie)
library(comprehenr)

mat <- mat2
mat[p.mat2>=0.05] <- 0
mat[mat<0.5&mat>-0.5] <- mat[mat<0.5&mat>-0.5]/5
network <- graph_from_adjacency_matrix(mat, weighted=T, mode="undirected", diag=F)
edge.color <- factor(c("#FF681E", "#001164")[(E(network)$weight<0)+1])
tab <- table(moduleColors) %>% as.data.frame
node.size <- tab[match(rownames(mat), tab$moduleColors),]$Freq
node.colors <- c("#00fff5","#8A553A","#A38DC9","pink","#07beb8","#FDFD96","#2E91E5","grey","grey60","tan","#ff5148","#44D044","#9eebe8","black","midnightblue","#e5097f","#FFA07A","greenyellow")

colors <-blueWhiteRed(100,gamma = 0.4)[cut(module_all, breaks = seq(-1.6, 1.6, len = 100),include.lowest = TRUE)]

colors_discovery <- data.frame(module = colnames(ME_dat),
                               color = colors[1:18],
                               levels = module_discovery)

colors_validation <- data.frame(module = colnames(ME_dat),
                               color = colors[19:36],
                               levels = module_validation)

e <- get.edgelist(network,names=FALSE)
l <- qgraph.layout.fruchtermanreingold(e,weights = E(network)$weight,
                                       vcount=vcount(network),
                                       area=1.9*(vcount(network)^2),
                                       #repulse.rad=(vcount(network)^2)
                                       )

sig1 <- symnum(p.discovery, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("***", "**", "*", "•", " "))
sig2 <- symnum(p.validation, corr = FALSE, na = FALSE, cutpoints = c(0, 
    0.001, 0.01, 0.05, 0.1, 1), symbols = c("***", "**", "*", "•", " "))


sig <- data.frame(sig1 = sig1, sig2 = sig2) %>% within(newsig <- paste(sig1,sig2, sep="    "))
sig<- sig$newsig

V(network)$D <- 1:18
V(network)$V <- 1:18
V(network)$x <- l[, 1]
V(network)$y <- l[, 2]
V(network)$radius <- log10(node.size)/3
V(network)$sig1 <- sig1
V(network)$sig2 <- sig2
#V(network)$sig <- sig


df <- as_data_frame(network, "vertices")
df$colors <- node.colors
df2 <- df
for(i in 1:18){
  tmp <- df[i,]
  df1 <- tmp[rep(seq_len(nrow(tmp)), each = node.size[i]-1), ]
  df2 <- rbind(df2,df1)
}
df2 <- df2 %>% mutate(distance_to_center = runif(nrow(df2), 0, 1)*radius*3,
                      direction = runif(nrow(df2), 0, 1)*2*pi,
                      x = x + distance_to_center*cos(direction),
                      y = y + distance_to_center*sin(direction))

colors1 <- colors_discovery[order(df$x),]$color
colors2 <- colors_validation[order(df$x),]$color
fill_color <- to_vec(for(i in 1:18) c(rep(colors2[i],181),rep(colors1[i],181)))

png(file=paste0(path_output,"/Figure_tmp.png"),res=900, units = 'in', width=12, height = 8)

p <- ggraph(network,layout=l) +
  geom_edge_density(aes(fill = edge.color)) + 
  scale_edge_fill_identity() +
  geom_edge_link0(alpha = abs((E(network)$weight)*3),
                  aes(edge_colour = E(network)$weight, 
                      #edge_width=2,
                      )
                  )+
  scale_edge_color_gradient2(name = "Link Strength", 
                             low = "#001164",
                             mid='white', 
                             high = "#FF681E", 
                             midpoint = 0, 
                             limit = c(-1,1)) +

  scale_edge_width(range = c(1, 5))+
  geom_node_point(fill =node.colors,
                  colour = 'black',
                  size=log10(node.size)*9,
                  shape = 21,alpha=0.1,stroke=NA) +
  geom_point(data = df2,aes(x = x, y = y), size = 0.25,alpha=0.9,
             col = df2$colors) +
  
  geom_scatterpie(aes(x=x, y=y,r = radius),
                  data = df,
                  cols=c('D','V'),
                  fill=fill_color,
                  pie_scale = 1,
                  )+
  geom_node_text(aes(label = sig1,x = x+radius*0.4, y = y),  colour = 'yellow', size=(log10(node.size)/5)*7,
                  show.legend = FALSE, family = "serif",angle = 90) +
  
    geom_node_text(aes(label = sig2,x = x-radius*0.4, y = y),  colour = 'yellow', size=(log10(node.size)/5)*7,
                  show.legend = FALSE, family = "serif",angle = 90) +
  coord_fixed()+
  theme_void()+
  theme(legend.position = "none") 
p
dev.off()

# library(grid)
# 
# png(file=paste0(path_output,"/Figure_tmp.png"),res=900, units = 'in', width=8, height = 12)
# grid.newpage()
# vp <- viewport(name = "rotate", angle = -90, width =8, height = 12)
# pushViewport(vp)
# print(p, vp = "rotate", newpage = FALSE)
# dev.off()

```

network all gene and modules

```{r}

network <- graph_from_adjacency_matrix(TOM1, weighted=T, mode="undirected", diag=F)
network <- simplify(network)

plot(network,vertex.label = '')
```

network brown module

```{r}

```

```{r}
library(ggraph)

hubgenes_CT <- ModuleHubgeneCT$gene
adj <- TOM1
#adj <- adj[brown_genes,brown_genes]
brown_module <- data.frame(genes=colnames(multiExpr[[1]]$data),module = moduleColors) %>% filter(module=='brown')
brown_genes <- brown_module$genes
tmp <- data.frame(brown = abs(geneModuleMembership[brown_genes,'MMbrown']),
                  genes = brown_genes)
brown_100 <- tmp[order(tmp$brown,decreasing =TRUE),][1:100,]$genes

adj <- adj[c(brown_100[brown_100%nin%hubgenes_CT],
                    hubgenes_CT[rev(1:length(hubgenes_CT))]),
           
           c(brown_100[brown_100%nin%hubgenes_CT],
                    hubgenes_CT[rev(1:length(hubgenes_CT))])]
diag(adj) <- NA
adj[adj < quantile(adj, probs = 0.3, na.rm = T)] = 0

network <- graph_from_adjacency_matrix(adj, weighted=T, mode="undirected", diag=F)
network <- simplify(network)


#png(file=paste0(path_output,"/Figure_brown.png"),res=900, units = 'in', width=11, height = 11)
ggraph(network, 
       layout = 'kk'
       ) +
  geom_edge_link0(width = (E(network)$weight)*1.1,
                    colour = "grey") +
    geom_node_point(
      fill = ifelse(V(network)$name%in%hubgenes_CT,'brown','darkgreen'),
      col = 'black',stroke=1.5,shape = 21,
                    size = ifelse(V(network)$name%in%hubgenes_CT,  25,5),
                    alpha=ifelse(V(network)$name%in%hubgenes_CT,  1,0.5)) +
    geom_node_text(label = ifelse(V(network)$name%in%hubgenes_CT,V(network)$name,''), 
                   family = "serif",color='white') + 
    theme_graph()
#dev.off()
```

```{r}
brown_module <- data.frame(genes=colnames(multiExpr[[1]]$data),module = moduleColors) %>% filter(module=='brown')
brown_genes <- brown_module$genes

tmp <- data.frame(brown = abs(geneModuleMembership[brown_genes,'MMbrown']),
                  genes = brown_genes)
brown100 <- tmp[order(tmp$brown,decreasing = T),][1:100,'genes']


adj <- TOM1
adj <- adj[brown_genes,brown_genes]

#adj <- adj[brown100,brown100]

diag(adj) <- NA
adj[adj < quantile(adj, probs = 0.3, na.rm = T)] = 0

color <- "brown"
nodesize <- 50
Hubsize=75
node_cutoff = 100
network <- graph.adjacency(adj, mode ="undirected", weighted=T)
coexp_genes <- c('CNIH4')
if(!is.null(coexp_genes)) {
  label_name <- V(network)$name
  label_name[which(label_name %nin% coexp_genes)] <- ""
  nodesize <- rep(nodesize,length(label_name))
  nodesize[which(label_name %in% coexp_genes)] <- Hubsize
  network <- set.vertex.attribute(network, "label_name", value=label_name)
  network <- set.vertex.attribute(network, "nodesize", value=nodesize)
}


network <- simplify(network)  # removes self-loops
if (!is.null(node_cutoff)) {
  # node_cutoff <- min(node_cutoff,length(degree(network)))
  # degree_cutoff <- sort(as.vector(degree(network)),decreasing = T)[node_cutoff]
  # deg_filter <- degree(network) < degree_cutoff
  
  deg_filter <- V(network)$name %nin% brown100
  network <- igraph::delete.vertices(network, deg_filter)
}
E(network)$width <- E(network)$weight
#png(file=paste0(path_output,"/Figure_brown_network.png"),res=900, units = 'in', width=10, height = 10)
plot(network,
     vertex.label = ifelse(V(network)$name%in%hubgenes_CT,V(network)$name,''),
     vertex.label.color = 'white',
     edge.width = E(network)$weight*2,
     vertex.color = ifelse(V(network)$name%in%hubgenes_CT,'brown','darkgreen'),
     vertex.size = ifelse(V(network)$name%in%hubgenes_CT, 25,10)
     )
#dev.off()
```

Draw with Cytoscape

```{r}
library(RCy3)
library(ggrepel)
library(igraph)

draw_wgcna_top_genes_module_network <- 
function(TOM,gene_list, node_cutoff = NULL , gradient_color=NULL,
         module_color = NULL,coexp_genes = NULL,PPI_genes = NULL,
         nodesize=50, Hubsize=75, title = NULL, collection = NULL){
  adj <- TOM
  adj <- adj[gene_list,gene_list]
  diag(adj) <- NA
  #max(adj, na.rm = T)
  adj[adj < quantile(adj, probs = 0.3, na.rm = T)] = 0
  #adj[adj != 1] = 0
  color <- module_color 
  network <- graph.adjacency(adj, mode ="undirected", weighted=T)
  if(!is.null(coexp_genes)) {
    label_name <- V(network)$name
    label_name[which(label_name %nin% coexp_genes)] <- ""
    nodesize <- rep(nodesize,length(label_name))
    nodesize[which(label_name %in% coexp_genes)] <- Hubsize
    network <- set.vertex.attribute(network, "label_name", value=label_name)
    network <- set.vertex.attribute(network, "nodesize", value=nodesize)
  }
  # V(network)$name
  ## adding atribute of gradient color
  # network <- set.vertex.attribute(network, "gradient_color", value=gradient_color)
  # network <- set.vertex.attribute(network, "gradient_color", value=gradient_color)
  # V(network)$gradient_color
  network <- simplify(network)  # removes self-loops
  V(network)$color <- color
  if (!is.null(node_cutoff)) {
    node_cutoff <- min(node_cutoff,length(degree(network)))
    degree_cutoff <- sort(as.vector(degree(network)),decreasing = T)[node_cutoff] 
    deg_filter <- degree(network) < degree_cutoff
    network <- igraph::delete.vertices(network, deg_filter)
  }
  E(network)$width <- E(network)$weight
  library(RCy3)
  cytoscapePing() ## open Cytoscape by cmd Cytoscape &
  createNetworkFromIgraph(network, title = title,
                          collection = paste0("Igraph Collection ", collection))
}
```

```{r}
# adjacency = adjacency(rbind(multiExpr[[1]]$data,multiExpr[[2]]$data),
#                       power = 5,type ="unsigned")
# TOM = TOMsimilarity(adjacency)
brown_module <- data.frame(genes=colnames(multiExpr[[1]]$data),module = moduleColors) %>%filter(module=='brown')
brown_genes <- brown_module$genes

hub_coexp_genes <- c("CNIH4", "ZAP70")

draw_wgcna_top_genes_module_network(TOM = TOM1, gene_list = brown_genes,node_cutoff = 50,
                    module_color = "brown", 
                    #gradient_color=gene_list_HR$Log_HR,
                    coexp_genes = hub_coexp_genes,
                    title = paste0("brown network"),
                    collection = "for Mortality in HIVneg")

```

```{r}
library(RCy3)
adj <- TOM1
adj <- adj[brown_genes,brown_genes]
diag(adj) <- NA
adj[adj < quantile(adj, probs = 0.3, na.rm = T)] = 0

network <- graph_from_adjacency_matrix(adj, weighted=T, mode="undirected", diag=F)
network <- simplify(network)

network <- delete.edges(
    network ,
    E(network )[E(network )$weight > 0 & E(network )$weight < 0.2]
)



cytoscapePing() ## open Cytoscape by cmd Cytoscape &
createNetworkFromIgraph(network, title = 'brown',
                        collection = paste0("Igraph Collection "))
```

scatter plot CNIH4 vs ZAP70, PLCG1, CTLA4

```{r}
library(ggpmisc)
library(ggpubr)
library(cowplot)
df <- vst_data %>%select(c('CNIH4','ZAP70','PLCG1','CTLA4'))
l <- c('ZAP70','PLCG1','CTLA4')
p = list()
for(i in 1:length(l)){
  p1<-ggplot(data=df, aes_string(x='CNIH4',y=as.name(l[i])))+
  geom_point(alpha=0.2,col='red')+
  theme_bw()+
  stat_poly_line(se=T) +
  stat_cor(cor.coef.name = "r",size = 7,method = 'spearman')+
  theme_bw()+ 
  ylab(paste0(as.name(l[i])," expression"))+
  xlab("CNIH4 expression")+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12))
  p[[i]]<-ggdraw(p1)
  
}

png(file=paste0(path_output,"/Figure4B_scatterplot_CNIH4vsZAP70_PLCG1_CTLA4.png"),res=600, units = 'in', width=21, height =7)#30:18
ggpubr::ggarrange(
p[[1]],p[[2]],
p[[3]],
ncol =3,nrow=1)
dev.off()


png(file=paste0(path_output,"/Figure4B_scatterplot_CNIH4vsCTLA4.png"),res=600, units = 'in', width=7, height =7)
p1
dev.off()
```

```{r}

```

other

```{r}
library(ggplot2)
library(ggpmisc)
df <- filter(vst_ptb_tbm,Type=='PTB') %>% select(c('CNIH4','CD274','CD58','CT_mean')) %>% mutate(CD274_CD58=CD274/CD58)

ggcorrplot(cor(df, use='pairwise.complete.obs',method = cor_method),
           p.mat = cor.pval.test(df, df, method=cor_method, use='pairwise.complete.obs'), 
           lab = T,
           lab_size = 2,
           insig="blank",
           outline.color = 'black')+
  theme(legend.position="right")+
  labs(fill="Corr")+
  theme(axis.text.x = element_text(face="bold", colour="black", size=12),
        axis.text.y = element_text(face="bold", colour="black", size=12),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12))+
  guides(fill = guide_colourbar(title = "Corr",
                                size=15,
                                barheight = 40))

ggplot(data=df, aes_string(x='CNIH4',y=as.name('CD274_CD58')))+
  geom_point(alpha=0.2,col='red')+
  theme_bw()+
  stat_poly_line(se=T) +
  stat_cor(cor.coef.name = "r",size = 7,method = 'spearman')+
  theme_bw()+ 
  ylab(paste0(as.name('CD58')," expression"))+
  xlab("CNIH4 expression")+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12))
  #scale_fill_gradientn(colors=natparks.pals("Acadia"),limit = c(-1,1))
```

```{r}
library(gtsummary)
df <- filter(vst_ptb_tbm,Type=='PTB') %>% mutate(Cavity = ifelse(Cavity_CXR=='N',0,1))
df %<>% mutate(Neutrophil_counts=WBC*NEUTLE*0.01,
                     log2_Neutrophil_counts=log2(Neutrophil_counts),
                     Lymphocyte_counts=WBC*LYMLE *0.01,
                     log2_Lymphocyte_counts=log2(Lymphocyte_counts),
                     Monocyte_counts=WBC*MONOLE*0.01,
                     log2_Monocyte_counts=log2(Monocyte_counts),
                     Eosinophil_counts=WBC*EOSLE*0.01,
                     log2_Eosinophil_counts=log2(Eosinophil_counts))

model1 <- lm(CNIH4~CT_mean, data = df)
summary(model1)
tbl_regression(model1,intercept = TRUE,estimate_fun = purrr::partial(style_ratio, digits = 3)) %>%
  bold_labels() %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>% as_flex_table() %>%
  flextable::save_as_docx(path=paste0(path_output,"/lm_CNIH4vsCT_mean.docx"))

model2 <- lm(CNIH4~CT_mean+Neutrophil_counts+Lymphocyte_counts+Monocyte_counts + Eosinophil_counts +CD274,data=df)
summary(model2)
tbl_regression(model2,intercept = TRUE,estimate_fun = purrr::partial(style_ratio, digits = 3)) %>%
  bold_labels() %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>% as_flex_table() %>%
  flextable::save_as_docx(path=paste0(path_output,"/lm_CNIH4vsAll.docx"))

model3 <- glm(Cavity~CNIH4+CD274+CD58+CT_mean,family=binomial(link='logit'),data=df)
summary(model3)
tbl_regression(model3,intercept = TRUE,estimate_fun = purrr::partial(style_ratio, digits = 3)) %>%
  bold_labels() %>%
  modify_column_unhide(columns = c(statistic, std.error))  %>% as_flex_table() %>%
  flextable::save_as_docx(path=paste0(path_output,"/glm_CavityvsCNIH4_CD274_CD58_CT_mean.docx"))
```

## 3. Main Analysis

### Heatmap

```{r}

library(lattice)

df <- vst_data %>% select(c('CNIH4','CD274','CD58','GeneXpert_Base','CT_mean', 'IFNG'))

x_tilde <- expand.grid(CD274=seq(min(df$CD274,na.rm=T), max(df$CD274,na.rm=T), length.out=100), 
                       CD58=seq(min(df$CD58,na.rm=T), max(df$CD58,na.rm=T), length.out=100))

model1 <- lm(CT_mean ~ CD274*CD58, data=df, 
             #family="binomial"
             )

model1 <- lm(CD274  ~ CD58 + CNIH4, data=df, 
             #family="binomial"
             )

summary(model1)
x_tilde$CT_value <- predict(model1, x_tilde, type="response")

ggplot(data=x_tilde, mapping = aes(x=CD274,y= CD58 )) + 
  geom_raster(data = x_tilde, mapping = aes(fill=CT_value)) + 
  scale_fill_distiller(palette = "RdYlBu",direction=1) +
  geom_point(data=df, aes(x=CD274,y= CD58,
                          color=GeneXpert_Base,size=CNIH4
                          ),alpha=0.5)+
  scale_color_manual(values = c("ND" = "grey",
                                "Low" = "#4575b4",
                                'Medium'='#ffffbf',
                                'High'='#d73027'))+
  theme_bw()

vst_data$CNIH4
```

### Correlation Analysis

### Scatter plot

```{r}
df <- vst_data %>% select(c('IL1B','IL6','IL8'))
p<-list()

for(i in 1:27){
p1<-ggplot(data=df, aes_string(x='CNIH4',y=as.name(colnames(df)[i])))+
  geom_point(alpha=0.2,col='red')+
  theme_bw()+
  stat_poly_line(se=T) +
  stat_cor(cor.coef.name = "r",size = 7,method = 'spearman')+
  theme_bw()+ 
  ylab(paste0(as.name(colnames(df)[i])," expression"))+
  xlab("CNIH4 expression")+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12))
  p[[i]]<-ggdraw(p1)
  ggdraw(p1)
}
```

```{r}
library(ggpmisc)
library(ggpubr)
df <- vst_data %>% select(c('CNIH4','IFNG'))
ggplot(data=df, aes(x=CNIH4,y=IFNG))+
  geom_point(alpha=0.2,col='red')+
  theme_bw()+
  stat_poly_line(se=T) +
  stat_cor(cor.coef.name = "r",size = 7,method = 'spearman')+
  theme_bw()+
  ylab(paste0(as.name('IFNG')," expression"))+
  xlab("CNIH4 expression")+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12))
```

#### CNIH4 vs lum la

```{r}
library(ggplotify)
gene_names<-c('CD274', 'CD86','PDCD1', 'ZAP70', 'PLCG1','CTLA4', 'CD80')
col=c("#395b85", 'white', "#FF681E")

df <- vst_data %>% select(c('CNIH4',gene_names)) %>% dplyr::rename('CD274/PD-L1'='CD274',
                                                                    'PDCD1/PD1'='PDCD1')
cor_method = 'spearman'
mat1 <- cor(df,
           use='pairwise.complete.obs',
           method = cor_method)

p.mat1 <- cor.pval.test(df, 
                       df, 
                       method=cor_method, 
                       use='pairwise.complete.obs')

labels1 <-round(mat1,2)
vals1 <- labels1
vals1[p.mat1 > 0.05] <- 0
labels1[p.mat1 > 0.05] <- ''

myBreaks <- c(seq(-1, 0, length.out=ceiling(1000/2) + 1),
              seq(1/1000, 1, length.out=floor(1000/2)))

p01 <- pheatmap(vals1,
               color = colorRampPalette(col)(1000),
               breaks=myBreaks,
               display_numbers=labels1,fontsize_number=13,cex = 1.2,
               show_colnames = F,
               legend = F,
               cluster_rows = F,cluster_cols = F)
# row.order <- p01$tree_row$order
# col.order <- p01$tree_col$order
###

cell_names <- c("Neutrophil_counts","Monocyte_counts","Lymphocyte_counts")
df <- merge(vst_data,clinical_2_discovery,by=0) %>% select(all_of(c('CNIH4',gene_names,cell_names))) %>% 
  dplyr::rename('CD274/PD-L1'='CD274',
                'PDCD1/PD1'='PDCD1')
df
mat2 <- cor( df,
             use='pairwise.complete.obs',
             method = cor_method)
p.mat2 <- cor.pval.test(df, 
                        df, 
                        method=cor_method, 
                        use='pairwise.complete.obs')

mat2 <- mat2[9:11,1:8]
#mat2 <- mat2[,col.order]
p.mat2 <- p.mat2[9:11,1:8]
#p.mat2<- p.mat2[,col.order]

labels2 <-round(mat2,2)
vals2 <- labels2
vals2[p.mat2 > 0.05] <- 0
labels2[p.mat2 > 0.05] <- ''

myBreaks <- c(seq(-1, 0, length.out=ceiling(1000/2) + 1),
              seq(1/1000, 1, length.out=floor(1000/2)))

p_tmp<-ggcorrplot(vals2,
           colors = col,
           lab = F, 
           show.legend = T,
           lab_size = 2,
           outline.color = 'black') + 
  guides(fill = guide_colourbar(title = "Corr",
                                title.position = "right",size=18,
                                barheight = 25))

leg <- ggpubr::get_legend(p_tmp)

p02 <- pheatmap(vals2,
               color = colorRampPalette(col)(1000),
               breaks=myBreaks,
               display_numbers=labels2,
               cluster_cols=F,
               cluster_rows=F,
               show_colnames = T,
               legend = F,fontsize_number=13,cellheight = 40,cex = 1.2,
               clustering_callback = callback)

p1 <- as.ggplot(p01)
p2 <- as.ggplot(p02)
p3 <- ggplot() + theme_void()

# CellCounts combined
k = 0.934
png(file=paste0(path_output,"/Figure_Corr_CNIH4vs7_1.png"),res=600, units = 'in',
    width = 8,
    height =8,)
#par(mar = c(5, 500, 5, 5)) # Set the margin on all sides to 6
grid.arrange(arrangeGrob(arrangeGrob(p1, p3,
                         widths = c(k,1-k)),
                         p2,
                         nrow=2,
                         heights = c(0.55,0.3)),
             ggpubr::as_ggplot(leg),
             widths = c(4,0.7),
             ncol=2)
dev.off()
```

### Hurdles Model

```{r}
library(brms)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(tidybayes)
library(broom)
library(dplyr)
library(ggplot2)
library(broom.mixed)

options(mc.cores = 1, brms.backend = "cmdstanr")

CHAINS <- 4
ITER <- 2000
WARMUP <- 1000
BAYES_SEED <- 1234

# Create a custom family that is logit if y = 0, normal/gaussian if not
hurdle_gaussian <- custom_family("hurdle_gaussian", 
                dpars = c("mu", "sigma", "hu"),
                links = c("identity", "log", "logit"),
                lb = c(NA, 0, NA),
                type = "real")

# Stan code
stan_funs <- "
  real hurdle_gaussian_lpdf(real y, real mu, real sigma, real hu) { 
    if (y == 0) { 
      return bernoulli_lpmf(1 | hu); 
    } else { 
      return bernoulli_lpmf(0 | hu) +  
             normal_lpdf(y | mu, sigma); 
    } 
  }
"
# Prepare Stan code for use in brm()
stanvars <- stanvar(scode = stan_funs, block = "functions")
#set_cmdstan_path('C:/Users/triettm/AppData/Local/R/win-library/4.3/.cmdstan/cmdstan-2.33.1')
set_cmdstan_path('C:/Users/triettm/OneDrive - Oxford University Clinical Research Unit/Documents/.cmdstan/cmdstan-2.34.0')

```

```{r}
library(parameters)

Fludigm_CNIH4_PTB <- get(load(paste0(path_input,'Raw_data/Fludigm_CNIH4_PTB.Rdata'))) %>% filter(GAPDH<15)

dim(Fludigm_CNIH4_PTB)# 171  12
hist(Fludigm_CNIH4_PTB$CT_Xpert_mean)

Fludigm_CNIH4_PTB %<>% mutate(
  bacterial_load_1 = log2(40/CT_Xpert_mean)
)

ggplot( Fludigm_CNIH4_PTB,aes(x = bacterial_load_1, y = CT_Xpert_mean))+
  geom_point()

hist(Fludigm_CNIH4_PTB$bacterial_load_1)

Hmisc::describe(Fludigm_CNIH4_PTB)


hist(Fludigm_CNIH4_PTB$log2_CT)
colnames(Fludigm_CNIH4_PTB)


model_hurdle_CNIH4 <- brm(
  bf(bacterial_load_1 ~ CNIH4_Norm,
     hu ~ CNIH4_Norm),
  data = Fludigm_CNIH4_PTB,
  family = hurdle_gaussian,  # <--- This is new
  stanvars = stanvars,   # <--- This is new
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  silent = 2
)

tidy(model_hurdle_CNIH4)
# non-hurdle: 0.103 [0.0249,0.183], p = 0.0090
# hurdle: -0.130, [-1.23, 0.955], p = 0.8085
p_value(model_hurdle_CNIH4) # 

pp_check(model_hurdle_CNIH4, ndraws = 500)

c_CNIH4 <- cbind.data.frame(
  data.frame(tidy(model_hurdle_CNIH4))[1:4,4:8],
  p.value=p_value(model_hurdle_CNIH4)[,2])

colnames(c_CNIH4)<-c("Parameter","Estimate","std.error","conf.low","conf.high","p_value")

summary(Fludigm_CNIH4_PTB$CNIH4_Norm)

newdata=data.frame(CNIH4_Norm=seq(min(Fludigm_CNIH4_PTB$CNIH4_Norm),max(Fludigm_CNIH4_PTB$CNIH4_Norm),len=50))

pred_CNIH4<-fitted(model_hurdle_CNIH4, newdata = newdata)

d_pred_CNIH4<-cbind(newdata,pred_CNIH4)


d_pred_CNIH4<-d_pred_CNIH4 %>% mutate(CT_pred=40/2^(Estimate),
              lower_pred=40/2^(Q2.5),
              upper_pred=40/2^(Q97.5))
dim(d_pred_CNIH4)# 50  8
summary(d_pred_CNIH4$CNIH4_Norm)
summary(d_pred_CNIH4$CT_pred)

p_CNIH4<-ggplot(data=d_pred_CNIH4,aes(x=CNIH4_Norm,y=CT_pred))+
  geom_line(size=2,col="#313695")+
  geom_ribbon(aes(ymin=lower_pred,ymax=upper_pred,x=CNIH4_Norm),alpha=0.4,fill="#313695")+
  scale_y_continuous(trans = log2_trans(),
    breaks = (seq(10,40,by=5)),
    labels = seq(10,40,by=5))+
  
  geom_jitter(data=Fludigm_CNIH4_PTB,aes(x = CNIH4_Norm, y = CT_Xpert_mean  ), size=2.5,alpha=0.5)+
  theme_bw()+
  #labs(x = paste("CNIH4 Norm"," expression level [log2 counts] "), y = "Ct value")+
  labs(x = paste("CNIH4 Norm"), y = "Ct value")+
  theme(panel.grid.minor = element_blank(),axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face="bold", colour="black", size=20),
        axis.text.y = element_text( colour="black", size=15),
        axis.text.x = element_text( colour="black", size=15),
        axis.ticks.x=element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=15),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=15))+coord_cartesian(ylim=c(10,40))
p_CNIH4
```

```{r}
library(parameters)
df1 <- vst_data %>%select(c('CNIH4','CT_mean')) %>% mutate(CT_Xpert_mean = CT_mean, CNIH4_Norm = CNIH4)
df2 <- Data_26_27_CT %>%select(c('CNIH4','NAT')) %>% mutate(CT_Xpert_mean = NAT, CNIH4_Norm = CNIH4)
df3 <- Fludigm_CNIH4_PTB %>%select(c('CNIH4_Norm','GAPDH','CT_Xpert_mean')) %>% filter(GAPDH<11)

dfList <- list(df1,df2,df3)
#pval <- c('p < 2e-16','p < 2e-16', 'p = 0.007')
xpos <- c(11,11.2,2.8)

i=2

df <- dfList[[i]]
df <- df %>% mutate(bacterial_load_1 = log2(40/CT_Xpert_mean))
model_hurdle_CNIH4 <- brm(bf(bacterial_load_1 ~ CNIH4_Norm,
                             hu ~ CNIH4_Norm),
                          data = df,
                          family = hurdle_gaussian,  # <--- This is new
                          stanvars = stanvars,   # <--- This is new
                          chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
                          silent = 2
                          )
tidy(model_hurdle_CNIH4)
p_value(model_hurdle_CNIH4)
pp_check(model_hurdle_CNIH4, ndraws = 500)

c_CNIH4 <- cbind.data.frame(data.frame(tidy(model_hurdle_CNIH4))[1:4,4:8],
                            p.value=p_value(model_hurdle_CNIH4)[,2])
colnames(c_CNIH4)<-c("Parameter","Estimate","std.error","conf.low","conf.high","p_value")

summary(df$CNIH4_Norm)

newdata=data.frame(CNIH4_Norm=seq(min(df$CNIH4_Norm),max(df$CNIH4_Norm),len=50))

pred_CNIH4<-fitted(model_hurdle_CNIH4, newdata = newdata)

d_pred_CNIH4<-cbind(newdata,pred_CNIH4)


d_pred_CNIH4<-d_pred_CNIH4 %>% mutate(CT_pred=40/2^(Estimate),
          lower_pred=40/2^(Q2.5),
          upper_pred=40/2^(Q97.5))
dim(d_pred_CNIH4)# 50  8
summary(d_pred_CNIH4$CNIH4_Norm)
summary(d_pred_CNIH4$CT_pred)

p <- ggplot(data=d_pred_CNIH4,aes(x=CNIH4_Norm,y=CT_pred))+
  geom_line(size=2,col="#5E81AC")+
  geom_ribbon(aes(ymin=lower_pred,ymax=upper_pred,x=CNIH4_Norm),alpha=0.4,fill="#5E81AC")+
  scale_y_continuous(trans = log2_trans(),
                     breaks = (seq(10,40,by=5)),
                     labels = seq(10,40,by=5))+
  geom_point(data=df,aes(x = CNIH4_Norm, y = CT_Xpert_mean), size=4,alpha=0.2,col = "#313695")+
  # xlab("CNIH4 relative to GAPDH")+
  xlab('CHIH4 expression level [log2 counts]')+
  ylab("Mtb Xpert CT value")+
  theme_bw()+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12)) +
  annotate(geom="text",label='atop(bold("p = 0.0085"))',x=xpos[i],y=37,size=7,
              col="black", parse = TRUE)

png(file=paste0(path_output,"/TBM_CNIH4.png"),res=400, units = 'in', width=5, height = 5)
p
dev.off()
```

### Regression Analysis

-   Regression CNIH4 \~ CT_mean

-   Regression CNIH4 \~ CT_mean + Neutrophil_counts + Lymphocyte_counts + Monocyte_counts + Eosinophil_counts +CD274

```{r}
library(gtsummary)
df <- filter(vst_ptb_tbm,Type=='PTB')
df %<>% mutate(Neutrophil_counts=WBC*NEUTLE*0.01,
                     log2_Neutrophil_counts=log2(Neutrophil_counts),
                     Lymphocyte_counts=WBC*LYMLE *0.01,
                     log2_Lymphocyte_counts=log2(Lymphocyte_counts),
                     Monocyte_counts=WBC*MONOLE*0.01,
                     log2_Monocyte_counts=log2(Monocyte_counts),
                     Eosinophil_counts=WBC*EOSLE*0.01,
                     log2_Eosinophil_counts=log2(Eosinophil_counts))

model1 <- lm(CNIH4~CT_mean, data = df)
tbl_regression(model1,intercept = TRUE,estimate_fun = purrr::partial(style_ratio, digits = 3)) %>%
  bold_labels() %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>% as_flex_table() %>%
  flextable::save_as_docx(path=paste0(path_output,"/lm_CNIH4vsCT_mean.docx"))

model2 <- lm(CNIH4~CT_mean+Neutrophil_counts+Lymphocyte_counts+Monocyte_counts + Eosinophil_counts +CD274,data=df)
tbl_regression(model2,intercept = TRUE,estimate_fun = purrr::partial(style_ratio, digits = 3)) %>%
  bold_labels() %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>% as_flex_table() %>%
  flextable::save_as_docx(path=paste0(path_output,"/lm_CNIH4vsAll.docx"))
```

### Differential Co-expression

```{r}
library(dcanr)

DiffCoexAnalysis <- function(data,gene_list,disease_type){
  df <- data %>% select(any_of(c(gene_list,'Type','CNIH4level'))) %>%filter(Type==disease_type)
  #df %<>% mutate(CNIH4level=ifelse(CNIH4level =='LOW',1, 2))
  cor_method = 'spearman'
  
  lowCNIH4_mat <- cor(df%>%filter(CNIH4level==1)%>%select(any_of(gene_list)),
                        use='pairwise.complete.obs',
                        method = cor_method)
  
  p.lowCNIH4_mat <- cor.pval.test(df%>%filter(CNIH4level==1)%>%select(any_of(TCR_gene_list)), 
                                  df%>%filter(CNIH4level==1)%>%select(any_of(TCR_gene_list)),
                                    method=cor_method,
                                    use='pairwise.complete.obs')
  
  highCNIH4_mat <- cor(df%>%filter(CNIH4level==2)%>%select(any_of(TCR_gene_list)),
                        use='pairwise.complete.obs',
                        method = cor_method)
  
  p.highCNIH4_mat <- cor.pval.test(df%>%filter(CNIH4level==2)%>%select(any_of(TCR_gene_list)), 
                                    df%>%filter(CNIH4level==2)%>%select(any_of(TCR_gene_list)), 
                                    method=cor_method, 
                                    use='pairwise.complete.obs')
  
  
  return(df)
}

gene_list <-c('TNFSF12','TSLP','TNFSF10','OSM','CSF1','LTA','IL33','IL27','IL18','IL17F','IL17A','IL15','IL13','CXCL8','IL7','IL6','IL4','IL2','CSF2','CSF3','FLT3LG','IL12A', 'IL12B', 'IL10', 'IL1B','IL6','IL4','IFNG','TNF')
df<-DiffCoexAnalysis(data=vst_ptb_tbm,gene_list = gene_list,disease_type='PTB')
View(df)
```

```{r}
library(dcanr)

#TCR_gene_list <-get_genelist_pathway_kegg('hsa04660')

TCR_gene_list <-c('TNFSF12','TSLP','TNFSF10','OSM','CSF1','LTA','IL33','IL27','IL18','IL17F','IL17A','IL15','IL13','CXCL8','IL7','IL6','IL4','IL2','CSF2','CSF3','FLT3LG','IL12A', 'IL12B', 'IL10', 'IL1B','IL6','IL4','IFNG','TNF') 

TCR_df <- vst_ptb_tbm %>% select(any_of(c(TCR_gene_list,'Type','CNIH4level'))) # Columns `PAK5`, `BUB1B-PAK6`, `IL2`, and `CSF2` don't exist.
colSums(is.na(TCR_df)) #Check NA
dim(TCR_df)
df <- filter(TCR_df,Type=='PTB')
#df <- df[order(df$CNIH4level,decreasing=FALSE, na.last=FALSE),]
df %<>% mutate(CNIH4level=ifelse(CNIH4level =='LOW',1, 2))

cor_method = 'spearman'
lowCNIH4_mat <- cor(df%>%filter(CNIH4level==1)%>%select(any_of(TCR_gene_list)),
                      use='pairwise.complete.obs',
                      method = cor_method)

p.lowCNIH4_mat <- cor.pval.test(df%>%filter(CNIH4level==1)%>%select(any_of(TCR_gene_list)), 
                                df%>%filter(CNIH4level==1)%>%select(any_of(TCR_gene_list)),
                                  method=cor_method, 
                                  use='pairwise.complete.obs')

highCNIH4_mat <- cor(df%>%filter(CNIH4level==2)%>%select(any_of(TCR_gene_list)),
                      use='pairwise.complete.obs',
                      method = cor_method)

p.highCNIH4_mat <- cor.pval.test(df%>%filter(CNIH4level==2)%>%select(any_of(TCR_gene_list)), 
                                  df%>%filter(CNIH4level==2)%>%select(any_of(TCR_gene_list)), 
                                  method=cor_method, 
                                  use='pairwise.complete.obs')

emat <- t(df%>%select(any_of(TCR_gene_list))) #tranpose
condition <- df$CNIH4level # high and low
scores <- dcScore(emat, 
                  condition,
                  dc.method = "zscore",
                  cor.method = 'spearman')
raw_p <- dcTest(scores, emat, condition)
raw_p[is.na(raw_p)] <- 1000
adj_p <- dcAdjust(raw_p, f = p.adjust, method = 'fdr')
```

```{r}
library(igraph)
library(qgraph)

col = c("#00b8ff","black","magenta")

highlow_mat <- highCNIH4_mat
highlow_mat[upper.tri(highCNIH4_mat,diag=F)] <- lowCNIH4_mat[upper.tri(lowCNIH4_mat,diag=F)]
p.highlow_mat <- p.highCNIH4_mat
p.highlow_mat[upper.tri(p.highCNIH4_mat,diag=F)] <- p.lowCNIH4_mat[upper.tri(p.lowCNIH4_mat,diag=F)]

p12<-ggcorrplot(highlow_mat[,dim(highlow_mat)[1]:1],
           p.mat = p.highlow_mat[,dim(highlow_mat)[1]:1], 
           lab = F,
           lab_size = 2,
           insig="blank",
           outline.color = 'black')+
  theme(legend.position="right")+
  labs(fill="Corr")+
  theme(axis.text.x = element_text(face="bold", colour="black", size=12),
        axis.text.y = element_text(face="bold", colour="black", size=12),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12))+
  guides(fill = guide_colourbar(title = "Corr",
                                size=15,
                                barheight = 40)) + 
  scale_fill_gradientn(colors=natparks.pals("Acadia"),limit = c(-1,1)) + annotate('segment', 
               x = dim(highlow_mat)[1] + .5, 
               xend = 0.5, 
               y = 0.5, 
               yend = dim(highlow_mat)[1] + .5, 
               color = 'black', size = 0.25)

tmp <- highlow_mat
#tmp[is.na(raw_p)] <- NA
tmp[raw_p >= 0.05] <- NA
tmp<-which(!is.na(tmp[dim(highlow_mat)[1]:1,]), arr.ind=T)

for(row in 1:nrow(tmp)) {
  i = tmp[row,]
  p12 <- p12 + annotate('rect', 
               xmin = i[2]-0.5, 
               xmax = i[2]+0.5, 
               ymin = i[1]-0.5, 
               ymax = i[1]+0.5,
           fill = NA, color = 'black', size = 0.5)
}

ggcorrplot(scores[,dim(highlow_mat)[1]:1],
           p.mat = raw_p[,dim(highlow_mat)[1]:1], 
           colors = col,
           show.diag = TRUE,
           lab = F, 
           lab_size = 2,
           insig="blank",
           #ggtheme =ggplot2::theme_void,
           outline.color = 'black',
           )

p3 <- ggcorrplot(scores[,dim(highlow_mat)[1]:1],
           p.mat = raw_p[,dim(highlow_mat)[1]:1], 
           colors = col,
           show.diag = TRUE,
           lab = F, 
           lab_size = 2,
           insig="blank",
           #ggtheme =ggplot2::theme_void,
           outline.color = 'black',
           ) +
  theme(legend.position="right")+
  labs(fill="Differential Z-scores")+
  scale_fill_gradient2(limit = c(-6,6), 
                       low = col[1], 
                       high =  col[3], 
                       mid = col[2], midpoint = 0)+
  
  theme(axis.text.x = element_text(face="bold", colour="black", size=12,angle = 45),
        axis.text.y = element_text(face="bold", colour="black", size=12,hjust = 1),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12,angle = -90,
                                     hjust = 0.5, vjust = 0.5),
        panel.border = element_rect(colour = "black", fill=NA, size=1,linewidth = 1)) +   
  guides(fill = guide_colourbar(title = "Differential Z-scores",
                                title.position = "right",size=15,
                                barheight = 40))
p3
############################################################################################
set.seed(7)
dcnet <- dcNetwork(scores,
                   raw_p,
                   thresh=0.05)

e <- get.edgelist(dcnet,names=FALSE)
l <- qgraph.layout.fruchtermanreingold(e,
                                       vcount=vcount(dcnet),
                                       area=15*(vcount(dcnet)^2),
                                       repulse.rad=(vcount(dcnet)^3.3)
                                       )
# Isolated = which(degree(dcnet)==0)
# dcnet = delete.vertices(dcnet, Isolated)
# l = l[-Isolated,]

png(file=paste0(path_output,"/Figure_dcnet_cytokine_PTB.png"),res=900, units = 'in', width=7, height = 7)
plot(dcnet,layout=l,
     vertex.size=2,
     vertex.label.cex = 0.5,
     vertex.label.dist=0.5,
     edge.width=1,
     main = 'Differential co-expression network',
     width=2,
     layout.rotate = 100,
     )

dev.off()

#########################################################################################
sigf_lowCNIH4_mat <- lowCNIH4_mat
sigf_lowCNIH4_mat[raw_p>=0.05] <- NA

sigf_highCNIH4_mat <- highCNIH4_mat
sigf_highCNIH4_mat[raw_p>=0.05] <- NA

low_corr <- sigf_lowCNIH4_mat[upper.tri(sigf_lowCNIH4_mat,diag=F)]
high_corr <- sigf_highCNIH4_mat[upper.tri(sigf_highCNIH4_mat,diag=F)]

low_high <- data.frame(low_corr,high_corr)
names(low_high) <- c('Low CNIH4','High CNIH4')

low_high_long <- pivot_longer(low_high,colnames(low_high))
names(low_high_long) <- c('CNIH4level','Coexpression')

p5<-ggplot(data=low_high_long,
       aes(x=fct_reorder(CNIH4level, Coexpression, .na_rm = TRUE,.desc =TRUE),
           y=Coexpression)) +
  theme_bw() +
  geom_violin(aes(color=CNIH4level,fill=CNIH4level),
              width=0.7,alpha=0.5,
              trim=FALSE)+
  scale_fill_manual(values=c("#B48EAD","#81A1C1"))+
  scale_color_manual(values=c("#B48EAD","#81A1C1"))+
  geom_boxplot(aes(color=CNIH4level),
               size=1,
               position=position_dodge(1),
               width=0.2,
               outlier.colour="red",
               outlier.shape=NA,outlier.size=3)+
    geom_jitter(aes(color=CNIH4level,fill=CNIH4level),
              width=0.05,
              height=0,
              size=2,
              alpha = 0.7)+
  labs(x="",y = "Absolute pairwise coexpression", title = "")+
  theme(plot.title = element_text(size = 25),
        legend.position = "none",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold"))+
  stat_compare_means( size = 5,
                      label.x = 1.3,
                      label.y = 1.3)

p5
```

### DESEQ2

```{r}
library(EnhancedVolcano)
library(comprehenr)

df <- filter(vst_ptb_tbm,Type=='PTB') %>% select(c('LIMS_ID','CNIH4level'))
PTB_sample_RNAseq <- All_sample_RNAseq %>% subset(Study %in% c("28TB","29TB"))
count_data <-count_all[,rownames(PTB_sample_RNAseq)]
count_data<-count_data[ , !(names(count_data) %in% c('HOA7818A92'))] # drop 1 patients not in vst

df<- df[order(df$LIMS_ID),] #col
df$CNIH4level<-factor(df$CNIH4level,levels=c(1,2))
df$LIMS_ID<-NULL

count_data<-count_data[ , order(names(count_data))]
anno_symbol <- anno[,c("gene_id", "gene_symbol")] %>% filter(gene_id %in% rownames(count_data))
rownames(anno_symbol) <- anno_symbol$gene_id
anno_symbol <- anno_symbol[rownames(count_data),]
count_data <- cbind(genenames=anno_symbol$gene_symbol,count_data)
count_data <-count_data %>% filter(genenames %in% names(RNA_data) & genenames!='CNIH4')

count_data$genenames<-NULL
anno_symbol <- anno[,c("gene_id", "gene_symbol")] %>% filter(gene_id %in% rownames(count_data))

dup_genes_id <- anno_symbol[duplicated(anno_symbol$gene_symbol), ]$gene_id
count_data <- count_data[!(rownames(count_data) %in% dup_genes_id),]

dds <- DESeqDataSetFromMatrix(count_data, colData=df, ~CNIH4level)
dds <- DESeq(dds)

#results(dds, contrast=c("condition","C","B")) meaning genes with:
#logFC > 0 are overexpressed in C and underexpressed in B.
#logFC < 0 means underexpressed in C and overexpressed in B

res1 <- results(dds,contrast=c('CNIH4level',2,1),alpha=0.05)
#res2 <- lfcShrink(dds, coef= 'CNIH4level_2_vs_1', type="apeglm")
summary(res1)

labels <- mapvalues(rownames(res1), 
          from=anno_symbol$gene_id, 
          to=anno_symbol$gene_symbol)

EnhancedVolcano(res1,
    lab = labels,
    x = 'log2FoldChange',labSize = 2.0,
    pCutoff = 0.05,
    FCcutoff = log2(1.5),
    y = 'padj',)

get_DEGgenes <- function(df,reg){
    if(reg=='high'){
      key <- intersect(rownames(df)[which(df$log2FoldChange>=log2(1.5))], rownames(df)[which(df$padj<0.05)])
    }
    if(reg=='low'){
      key <- intersect(rownames(df)[which(df$log2FoldChange<=-log2(1.5))], rownames(df)[which(df$padj<0.05)])
    }
    results <- as.data.frame((df)[which(rownames(df) %in% key),])
    return(results)
}

deg_high <- rownames(get_DEGgenes(as.data.frame(res1),reg='high'))
deg_low <- rownames(get_DEGgenes(as.data.frame(res1),reg='low'))

deg_high <- to_vec(for(i in 1:length(deg_high)) filter(anno_symbol,gene_id==deg_high[i])$gene_symbol)
deg_low <- to_vec(for(i in 1:length(deg_low)) filter(anno_symbol,gene_id==deg_low[i])$gene_symbol)
```

### Pathway Analysis

```{r}
ORA_bar_plot <- function(df,name,n=5){
  n <- min(nrow(df),n)
  df <- df[1:n,]
  #n_break <- as.integer(max(df$log_pvalue))
  p <- ggplot(aes(x= ID,y = log_pvalue),data =df) + 
  geom_col(position = "stack", 
           alpha = 0.5,fill="#4292c6") +
  geom_text(aes(x=ID,y=0.1,label =ID), 
            size=3,fontface='bold',hjust=0)+
  ggtitle(name)+
  #geom_text(aes(x=ID,y=pos,label =log_pvalue), hjust=0.5) +
  #scale_y_continuous(breaks = 1:n_break)+ 
  coord_flip()+
  labs(x="", y="Log10 P value") +
  #scale_fill_manual(values=c("#4292c6")) +
  theme_bw()+
  theme(plot.title = element_text(size = 20),
        legend.text = element_text(size = 15) ,
        legend.position="right",
        legend.title = element_text(size = 13,color="black",face="bold"),
        axis.text.x=element_text(color="black",size=13),
        axis.title.x = element_text(size = 13,color="black",face="bold"),
        axis.text.y=element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_text(size = 13,color="black",face="bold"))
  
  #p
  return(p)
}
```

```{r}
library(msigdbr)
library(dplyr)
library(clusterProfiler)
# db <- msigdbr(species = "Homo sapiens", category = "H") %>%
#   dplyr::select(gs_name, human_gene_symbol)
#C5, C8

# db <- msigdbr(species = "Homo sapiens", category = "C5") %>%
#   filter(gs_subcat=="GO:BP") %>% #C5
#   dplyr::select(gs_name, human_gene_symbol)

db <- msigdbr(species = "Homo sapiens", category = "C8") %>%
  dplyr::select(gs_name, human_gene_symbol)

dim(db)

ORA_analysis <- function(gene_list){
  temp <- enricher(gene_list, TERM2GENE=db, pvalueCutoff = 1, qvalueCutoff = 1)
  temp <- temp@result
  if(!is.na(table(temp$p.adjust < padj)["TRUE"]) &  table(temp$p.adjust < padj)["TRUE"]>10){
    temp <- temp %>% filter(p.adjust<padj) %>%
    dplyr::arrange(pvalue)
    } 
  else{
    temp <- temp %>%
    dplyr::arrange(pvalue)
    temp <- temp[1:min(nrow(temp),10),]
    }
  # df <- temp %>%
  # dplyr::arrange(pvalue) %>%
  # dplyr::mutate(log_pvalue=-log10(pvalue),
  #               pos = ifelse(log_pvalue <4,log_pvalue + 1,log_pvalue + 0.5))
  # ORA_bar_plot(df)
  return(temp)
}

ora_low <- ORA_analysis(deg_low)
df1 <- ora_low %>%
  dplyr::arrange(pvalue) %>%
  dplyr::mutate(log_pvalue=-log10(pvalue),
                pos = ifelse(log_pvalue <4,log_pvalue + 1,log_pvalue + 0.5))
p1<-ORA_bar_plot(df1,'Genes down-regulated in high CNIH4')
p1
ora_high <- ORA_analysis(deg_high)
df2 <- ora_high %>%
  dplyr::arrange(pvalue) %>%
  dplyr::mutate(log_pvalue=-log10(pvalue),
                pos = ifelse(log_pvalue <4,log_pvalue + 1,log_pvalue + 0.5))
p2<-ORA_bar_plot(df1,'Genes up-regulated in high CNIH4')


n = 5
df1 <- df1[1:min(nrow(df1),n),] %>% mutate(group='downregulated genes') %>% arrange(ID)
df2 <- df2[1:min(nrow(df2),n),] %>% mutate(group='upregulated genes') %>% arrange(ID)
df <- rbind(df1,df2)
df$ID <- factor(df$ID, levels = df$ID)

#n_break <- as.integer(max(df$log_pvalue))
p <- ggplot(data =df,aes(x= ID,y = log_pvalue,fill=group)) + 
  geom_col(position = 'stack',
         alpha = 0.5,
         aes(x=ID,y = log_pvalue,
             fill = group)) +
scale_fill_manual( values = c('#5E81AC','#BF616A'))+
geom_text(aes(x=ID,y=0.1,label =ID), 
          size=3,fontface='bold',hjust=0)+
#geom_text(aes(x=ID,y=pos,label =log_pvalue), hjust=0.5) +
#scale_y_continuous(breaks = 1:n_break)+ 
coord_flip()+
labs(x="", y="Log10 P value") +
#scale_fill_manual(values=c("#4292c6")) +
theme_bw()+
theme(plot.title = element_text(size = 20),
      legend.text = element_text(size = 15) ,
      legend.position="right",
      legend.title = element_text(size = 13,color="black",face="bold"),
      axis.text.x=element_text(color="black",size=13),
      axis.title.x = element_text(size = 13,color="black",face="bold"),
      axis.text.y=element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_text(size = 13,color="black",face="bold"))
p
```

```{r}
for(i in 1:2){
  print(i)
}
```
