---
title: "PTB_FinalMainAnalysis"
author: "Triet Thai"
date: "2024-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PTB Transcriptomics Project

## 1. Import libraries and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE)

library(parallel)
mcore<-1 # for Window PC

#Load libraries
library(dplyr)
library(plyr)
library(readxl)
library(writexl)
library(survival)
library(glmnet)
library(stabs)
library(tidyverse)
library(magrittr)
library(Hmisc)
library(gtsummary)
library(WGCNA)
library(ggcorrplot)
library(scales)
library(gridExtra)
library(ggcorrplot)
library(broom)
library(rms)
library(tidyverse)
library(stabs)
library(mboost)
library(DESeq2)
library(CEMiTool)
library(igraph)
library(flextable)
library(pheatmap)
library(ggplot2)
library(ggplotify)
path_input <- paste0(str_replace_all(Sys.getenv("USERPROFILE"), '\\\\', '/'),
                     "/OneDrive - Oxford University Clinical Research Unit/#OUCRU-TB/#oucru-tb/PTB_project/")
path_output<-paste0(str_replace_all(Sys.getenv("USERPROFILE"), '\\\\', '/'),
                     "/OneDrive - Oxford University Clinical Research Unit/#OUCRU-TB/#oucru-tb/PTB_project/Triet_Results")
```

```{r}


load(paste0(path_input,"/Raw_data/vst_Gensymbol_allPTB_295Sample_18Feb22.RData")) #vst_data 295 31425
load(paste0(path_input,"/Raw_data/vst_Gensymbol_allTBM_281Sample_12Jan24.RData")) #tbm_vst 281 31381
rownames(tbm_vst) <- tbm_vst$LIMS_ID
load(paste0(path_input,"/Data/Fluidigm_PTB_data.Rdata"))
load(paste0(path_input,"/Data/Most_variance_RNA_genes.Rdata"))
load(file=paste0(path_input,"Raw_data/count_data_adjusted_ComBat.Rdata"))
load(paste0(path_input, "Raw_data/Data_RNAseq_RUN1andRUN2_15Feb2023.RData"))
All_sample_RNAseq <- readxl::read_excel(paste0(path_input,"Raw_data/All_sample_RNAseq.xlsx"),
                                        sheet = "Run1and2") %>% as.data.frame()
rownames(All_sample_RNAseq) <- All_sample_RNAseq$LIMS_ID

load(file=paste0(path_input,"Raw_data/Data_26_27_CT_CNIH4.Rdata.RData"))
Fludigm_CNIH4_PTB <- get(load(paste0(path_input,'Raw_data/Fludigm_CNIH4_PTB.Rdata')))

ModuleHubgeneCT <- read.csv(paste0(path_input,"Data/Modules-Hubgenes_CT_value.csv"))
load(file=paste0(path_input,"Data/Gene Significance and Module Membership_clinical_trait.Rdata"))
load(file = paste0(path_input,"Data/PTB-01-dataInput.RData"))
load(file = paste0(path_input,"Data/PTB-02-networkConstruction-auto.RData"))
load(file = paste0(path_input,"Data/Module_discovery.Rdata"))
load(file=paste0(path_input,"Raw_data/PTB_TOM_10000-block.1.RData"))
TOM1 <- as.matrix(TOM)
colnames(TOM1) <- colnames(multiExpr[[1]]$data)
rownames(TOM1) <- colnames(multiExpr[[1]]$data)

clinical_2_discovery <- filter(clinical_2, cohort=='Discovery')
rownames(clinical_2_discovery) <- clinical_2_discovery$LIMS_ID


###------ImputeCIBERSORT------###
impute_df <-  read.csv(paste0(path_input,'/Raw_data/CIBERSORTx_Adjusted_CPM_LM22.txt'),sep='\t') %>% filter(P.value<0.05)
rownames(impute_df) <- impute_df$Mixture
impute_df$Mixture <- NULL
```

```{r}
vst_ptb_tbm <- rbind.fill(vst_data,tbm_vst)
vst_ptb_tbm %<>% mutate(Type=ifelse(LIMS_ID %in% vst_data$LIMS_ID,"PTB","TBM"))

healthy_ComBat <- count_data_adjusted_ComBat %>% filter(LIMS_ID %in% filter(Cli_All,trial_number %in% c('HV','43TB'))$LIMS_ID)
qt <- quantile(healthy_ComBat$CNIH4,c(0.75)) #Q3 CNIH4 of healthy control

PTB_TBM_ComBat <- count_data_adjusted_ComBat %>% filter(LIMS_ID %in% filter(Cli_All,(Timepoint=='D0') & (trial_number %in% c('MDR_PTB','DS_PTB','26TB','27TB')))$LIMS_ID)
PTB_TBM_ComBat %<>% mutate(CNIH4level=ifelse((CNIH4<qt[1]),1,2))

vst_ptb_tbm <- merge(vst_ptb_tbm,PTB_TBM_ComBat %>% select('LIMS_ID','CNIH4level'),by="LIMS_ID")
rownames(vst_ptb_tbm) <- vst_ptb_tbm$LIMS_ID
```

```{r}
healthy_df <- count_data_adjusted_ComBat %>% filter(LIMS_ID %in% filter(Cli_All,trial_number=='HV'|trial_number=='43TB')$LIMS_ID)
qt<-quantile(healthy_df$CNIH4,c(0.75)) #Q3 CNIH4 of healthy control

PTB_df <- count_data_adjusted_ComBat %>% filter(LIMS_ID%in%filter(Cli_All,trial_number=='MDR_PTB'|trial_number=='DS_PTB')$LIMS_ID)

# tmp <- PTB_df %>% select(CNIH4) %>% mutate(level=ifelse((CNIH4<qt[1]),"LOW",'HIGH'))

tmp <- PTB_df %>% select(CNIH4) %>% mutate(level=ifelse((CNIH4<qt[1]),1,2))

rownames(tmp) <- PTB_df$LIMS_ID
table(tmp$level) # 244 52
vst_data2<-merge(vst_data,tmp[,2, drop=FALSE],by=0)
rownames(vst_data2) <- vst_data2$LIMS_ID
dim(vst_data2) # 295 31427
```

```{r}
PTB_TBM_ComBat
```

## 2. Helper functions

```{r}
posterior_predict_hurdle_gaussian <- function(i, prep, ...) {
  mu <- brms::get_dpar(prep, "mu", i = i)
  sigma <- brms::get_dpar(prep, "sigma", i = i)
  theta <- brms::get_dpar(prep, "hu", i = i)
     
  hu <- runif(prep$ndraws, 0, 1)
  ifelse(hu < theta, 0, rnorm(prep$ndraws, mu,sigma))
}
   
posterior_epred_hurdle_gaussian <- function(prep) {
  with(prep$dpars, mu * (1 - hu))
}

cor.pval.test <- function(x1, x2, ...) {
  r <- ncol(x1)
  n <- ncol(x2)
  p.mat<- matrix(NA, r, n)
  for (i in 1:r) {
    for (j in 1:n) {
      tmp <- cor.test(x1[, i], x2[, j], ...)
      p.mat[i, j] <- tmp$p.value
    }
  }
  rownames(p.mat) <-  colnames(x1)
  colnames(p.mat) <- colnames(x2)
  return(p.mat)
}

anno_gene_symbol <- function(data,data_anno,export, name=NULL){
  anno_DESeq2 <- data_anno[,c("gene_id", "gene_symbol")]
  anno_DESeq2 <- subset(anno_DESeq2, gene_id %in% data$gene_id)
  data
  return(data)
}

get_genelist_pathway_kegg <- function(hsa_ID){
  library("KEGGREST")
  names <- keggGet(hsa_ID)[[1]]$GENE
  namesodd <-  names[seq(0,length(names),2)]
  namestrue <- gsub("\\;.*","",namesodd)
}

draw_colnames_45 <- function (coln, gaps, ...) {
    coord <- pheatmap:::find_coordinates(length(coln), gaps)
    x     <-  coord$coord - 0.5 * coord$size
    res   <- grid::textGrob(
      coln, x = x, y = unit(1, "npc") - unit(3,"bigpts"),
      vjust = 0.75, hjust = 1, rot = 45, gp = grid::gpar(...)
    )
    return(res)
}

assignInNamespace(
  x = "draw_colnames",
  value = "draw_colnames_45",
  ns = asNamespace("pheatmap")
)

# Modify ordering of the clusters using clustering callback option
callback <- function(hc, mat){
    sv = svd(t(mat))$v[,1]
    dend = reorder(as.dendrogram(hc), wts = sv)
    as.hclust(dend)
}

make_face_names <- function(mat, rc_fun, rc_names_b = NA, 
                            rc_names_i = NA) {
  f_names <- rc_fun(mat)
  ids_b <- rc_names_b %>% match(rc_fun(mat))
  ids_i <- rc_names_i %>% match(rc_fun(mat))
  
  ids_b %>%
    walk(
      function(i)
        f_names[i] <<-
        bquote(bold(.(rc_fun(mat)[i]))) %>%
        as.expression()
    )
  ids_i %>%
    walk(
      function(i)
        f_names[i] <<-
        bquote(italic(.(rc_fun(mat)[i]))) %>%
        as.expression()
    )
  
  f_names
}

color.bar <- function(lut, min, max=-min, nticks=11, ticks=seq(min, max, len=nticks), title='') {
  scale = (length(lut)-1)/(max-min)
  plot(c(0,10), c(min,max), type='n', bty='n', xaxt='n', xlab='', yaxt='n', ylab='', main=title)
  axis(2, ticks, las=1)
  for (i in 1:(length(lut)-1)) {
    print(lut[i])
    y = (i-1)/scale + min
    rect(0,y,10,y+1/scale, col=lut[i], border=NA)
  }
}
```

### 3. Main Analysis

### 3.1. Correlation Heatmap CNIH4 vs 27 ICs

```{r}
IC_names<-c('CD200', 'CD2','CD58','TNFSF4', 'CD200R1', 'IDO1','TNFRSF18', 'TNFSF18',
             'CD28','BTLA', 'CD27', 'HAVCR2', 'CD274', 'TNFSF14', 'TNFRSF4',
             'CD276', 'TNFRSF14', 'PDCD1', 'CD86', 'TNFSF9', 'TIGIT','CD80',
             'ICOS', 'TNFRSF9', 'CTLA4', 'LAG3','LGALS9',
            'TMED9','TGFA','GLI1','CNIH4')
ICvsCNIH4_df <- vst_data %>% select(IC_names)
ICvsCNIH4_df <- ICvsCNIH4_df[vapply(ICvsCNIH4_df, 
                                    function(x) length(unique(x)) > 1, 
                                    logical(1L))] %>% dplyr::rename('HAVCR2/TIM-3'='HAVCR2',
                                                                    'CD274/PDL1'='CD274',
                                                                    'LGALS9/Galactin-9'='LGALS9',
                                                                    'PDCD1/PD1'='PDCD1')

cor_method = 'spearman'
ICvsCNIH4_mat <- cor(ICvsCNIH4_df,
                      use='pairwise.complete.obs',
                      method = cor_method)

p.ICvsCNIH4_mat <- cor.pval.test(ICvsCNIH4_df, 
                                  ICvsCNIH4_df, 
                                  method=cor_method, 
                                  use='pairwise.complete.obs')

#col=c("#001164", 'white', "#FF681E")
#col=c("#5E81AC", '#EBCB8B', "#BF616A")
col=c("#395b85", 'white', "#FF681E")
# CNIH4 vs 25 ICs
mat1 <- ICvsCNIH4_mat
p.mat1 <- p.ICvsCNIH4_mat
labels1 <-round(mat1,2)
vals1 <- labels1
vals1[p.mat1 > 0.05] <- 0
labels1[p.mat1 > 0.05] <- ''

myBreaks <- c(seq(-1, 0, length.out=ceiling(1000/2) + 1),
              seq(1/1000, 1, length.out=floor(1000/2)))

p01 <- pheatmap(vals1,
               color = colorRampPalette(col)(1000),
               breaks=myBreaks,
               display_numbers=labels1,
               show_colnames = F,legend = F)
p01
row.order <- p01$tree_row$order
col.order <- p01$tree_col$order
p1 <- as.ggplot(p01)
```

### 3.2.0. Custom

```{r}

df <- vst_data %>%select('CNIH4','TGFA')

p1<-ggplot(data=df, aes(x=CNIH4,y=TGFA))+
  geom_point(alpha=0.2,col='red')+
  theme_bw()+
  stat_poly_line(se=T) +
  stat_cor(cor.coef.name = "r",size = 7,method = 'spearman')+
  theme_bw()+ 
  ylab(paste0(as.name(colnames(df)[i])," expression"))+
  xlab("CNIH4 expression")+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12))
p1
```

### 3.2. Scatter plot CNIH4 vs 27 ICs

```{r}
library(ggpmisc)
library(ggpubr)
library(cowplot)

IC_names<-c('CD200', 'CD2','CD58','TNFSF4', 'CD200R1', 'IDO1','TNFRSF18', 'TNFSF18',
             'CD28','BTLA', 'CD27', 'HAVCR2', 'CD274', 'TNFSF14', 'TNFRSF4',
             'CD276', 'TNFRSF14', 'PDCD1', 'CD86', 'TNFSF9', 'TIGIT','CD80',
             'ICOS', 'TNFRSF9', 'CTLA4', 'LAG3','LGALS9','CNIH4')
df <- vst_data %>%select(IC_names) %>% dplyr::rename('HAVCR2/TIM-3'='HAVCR2',
         'CD274/PDL1'='CD274',
         'LGALS9/Galactin-9'='LGALS9',
         'PDCD1/PD1'='PDCD1'
         ) #295 patients

p<-list()

for(i in 1:27){
p1<-ggplot(data=df, aes_string(x='CNIH4',y=as.name(colnames(df)[i])))+
  geom_point(alpha=0.2,col='red')+
  theme_bw()+
  stat_poly_line(se=T) +
  stat_cor(cor.coef.name = "r",size = 7,method = 'spearman')+
  theme_bw()+ 
  ylab(paste0(as.name(colnames(df)[i])," expression"))+
  xlab("CNIH4 expression")+
  theme(plot.title = element_text(size = 15),
        legend.position = "none",
        axis.text = element_text(size = 15),
        axis.text.x=element_text(color="black",size=13,face="bold"),
        axis.title.x = element_text(size = 15,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=15),
        axis.title.y = element_text(size = 15,color="black",face="bold"),
        legend.text = element_text(size = 15),
        legend.title = element_text( colour="black", size=12),
        legend.key = element_rect(colour = NA),
        strip.text=element_text(face = "bold",size=12))
  p[[i]]<-ggdraw(p1)
  ggdraw(p1)
}

#png(file=paste0(path_output,"/Figure4B_scatterplot_CNIH4vsICs_all_PTB.png"),res=600, units = 'in', width=45, height =30)#30:18
ggpubr::ggarrange(
p[[1]],p[[2]],
p[[3]],p[[4]],
p[[5]],p[[6]],
p[[7]],p[[8]],
p[[9]],p[[10]],
p[[11]],p[[12]],
p[[13]],p[[14]],
p[[15]],p[[16]],
p[[17]],p[[18]],
p[[19]],p[[20]],
p[[21]],p[[22]],
p[[23]],p[[24]],
p[[25]],p[[26]],
p[[27]],
ncol =6,nrow=5)
#dev.off()
```

### 3.3. Hurdles Model PTB vs TBM vs PCR

```{r}
{r}
library(brms)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(tidybayes)
library(broom)
library(dplyr)
library(ggplot2)
library(broom.mixed)

options(mc.cores = 1, brms.backend = "cmdstanr")

CHAINS <- 4
ITER <- 2000
WARMUP <- 1000
BAYES_SEED <- 1234

# Create a custom family that is logit if y = 0, normal/gaussian if not
hurdle_gaussian <- custom_family("hurdle_gaussian", 
                dpars = c("mu", "sigma", "hu"),
                links = c("identity", "log", "logit"),
                lb = c(NA, 0, NA),
                type = "real")

# Stan code
stan_funs <- "
  real hurdle_gaussian_lpdf(real y, real mu, real sigma, real hu) { 
    if (y == 0) { 
      return bernoulli_lpmf(1 | hu); 
    } else { 
      return bernoulli_lpmf(0 | hu) +  
             normal_lpdf(y | mu, sigma); 
    } 
  }
"
# Prepare Stan code for use in brm()
stanvars <- stanvar(scode = stan_funs, block = "functions")
#set_cmdstan_path('C:/Users/triettm/AppData/Local/R/win-library/4.3/.cmdstan/cmdstan-2.33.1')
set_cmdstan_path('C:/Users/triettm/OneDrive - Oxford University Clinical Research Unit/Documents/.cmdstan/cmdstan-2.34.0')
```

#### 3.3.1. CNIH4 vs Ct value in PTB patients

#### 3.3.2. CNIH4 vs Ct value in TBM patients

#### 3.3.3. CNIH4 vs Ct value in PCR patients

### 3.4. Deconvolution Analysis

#### 3.4.1. CIBERSORT Cell pops

```{r}
library(ggpubr)
library(rstatix)

healthy_df <- count_data_adjusted_ComBat %>% filter(LIMS_ID %in% filter(Cli_All,trial_number=='HV'|trial_number=='43TB')$LIMS_ID)
rownames(healthy_df) <- healthy_df$LIMS_ID

PTB_df <- count_data_adjusted_ComBat %>% filter(LIMS_ID%in%filter(Cli_All,trial_number=='MDR_PTB'|trial_number=='DS_PTB')$LIMS_ID)
rownames(PTB_df) <- PTB_df$LIMS_ID

TBM_df <- count_data_adjusted_ComBat %>% filter(LIMS_ID%in%filter(Cli_All,(trial_number=='26TB'|trial_number=='27TB')&(Timepoint=='D0'))$LIMS_ID)
rownames(TBM_df) <- TBM_df$LIMS_ID

tmp1 <- merge(impute_df,healthy_df,by=0) %>% select(B.cells.naive:Neutrophils)
dim(tmp1)
tmp1 <- pivot_longer(tmp1,B.cells.naive:Neutrophils)
tmp1$group <- rep('Healthy',each=dim(tmp1)[1])

tmp2 <- merge(impute_df,PTB_df,by=0) %>% select(B.cells.naive:Neutrophils)
dim(tmp2)
tmp2 <- pivot_longer(tmp2,B.cells.naive:Neutrophils)
tmp2$group <- rep('PTB',each=dim(tmp2)[1])

tmp3 <- merge(impute_df,TBM_df,by=0) %>% select(B.cells.naive:Neutrophils)
dim(tmp3)
tmp3 <- pivot_longer(tmp3,B.cells.naive:Neutrophils)
tmp3$group <- rep('TBM',each=dim(tmp3)[1])



tmp<-rbind(tmp1,tmp2,tmp3)

stat.test <- tmp %>%
  group_by(name) %>% 
  t_test(value ~ group) %>% 
  add_significance("p") %>%
  add_xy_position(x = "name")

p <- ggplot(data=tmp,
       aes(x=name,y=value, color=factor(group, level = c('Healthy','PTB','TBM'))))+
  geom_boxplot() +
  geom_point(position=position_jitterdodge(jitter.width =0.3),
             alpha=0.1)+
  scale_color_manual(values=c("#81A1C1","#B48EAD","#A3BE8C"))+
  labs(color='Group')+ 
  xlab('Cell type')+
  ylab('% Cell population')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold")) +
  stat_pvalue_manual(stat.test, label = 'p.signif', tip.length = 0)

# png(file=paste0(path_output,"/Figure_CellPop_HealthyvsPTBvsTBM.png"),res=900, units = 'in', width=17, height = 9)
# p
# dev.off()
```

#### 3.4.2. CIBERSORT CNIH4

```{r}
impute_df
```

```{r}
df <- filter(vst_ptb_tbm,Type=='PTB') %>% select(c('LIMS_ID','CNIH4level'))

tmp <- merge(impute_df,df,by=0) %>% select(c(B.cells.naive:Neutrophils,CNIH4level))
tmp <- pivot_longer(tmp,B.cells.naive:Neutrophils)

# p<-ggplot(data=tmp,
#        aes(x=name,y=value))+
#   geom_boxplot(aes(color=name)) +
#   geom_jitter(height=0,aes(color=name),alpha=0.1)+
#   xlab('Cell type')+
#   ylab('% Cell population')+
#   theme_bw()+
#   theme(plot.title = element_text(size = 25),
#         legend.position = "",
#         legend.text = element_text(size = 20) ,
#         legend.title  = element_text(size = 20,color="black",face="bold"),
#         axis.text = element_text(size = 25),
#         axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
#         axis.title.x = element_text(size = 20,color="black",face="bold"),
#         axis.text.y=element_text(color="black",size=20),
#         axis.title.y = element_text(size = 20,color="black",face="bold"),
#         axis.title= element_text(size = 40,color="black",face="bold"))
#   
# png(file=paste0(path_output,"/Figure_CellPop_All.png"),res=900, units = 'in', width=14, height = 9)
# p
# dev.off()

stat.test <- tmp %>%
  group_by(name) %>% 
  t_test(value ~ CNIH4level) %>% 
  add_significance("p") %>%
  add_xy_position(x = "name")

p <- ggplot(data=tmp,
       aes(x=name,y=value, color=factor(CNIH4level, level = c('LOW','HIGH'))))+
  geom_boxplot() +
  geom_point(position=position_jitterdodge(jitter.width =0.3),
             alpha=0.1)+
  scale_color_manual(values=c("#81A1C1","#B48EAD"))+
  labs(color='CNIH4 Level')+ 
  xlab('Cell type')+
  ylab('% Cell population')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold")) +
  stat_pvalue_manual(stat.test, label = 'p.signif', tip.length = 0)
p
```

#### 3.4.2. BayesPrism

#### 3.4.2.1. Cell Proportion

```{r}
bp.res_healthy <- get(load(file=paste0(path_input,"Data/bp.res_healthy.rdata")))
bp.res_ptb <- get(load(file=paste0(path_input,"Data/bp.res_ptb.rdata")))
bp.res_tbm <- get(load(file=paste0(path_input,"Data/bp.res_tbm.rdata")))
```

```{r}
get_theta <- function(bp) {
  theta <- get.fraction (bp=bp,
            which.theta="final",
            state.or.type="type")
  theta <- as.data.frame(theta)
  row.names(theta) <- gsub("X", "", row.names(theta))
  row.names(theta) <- gsub("_PBMC", "", row.names(theta))
  theta <- theta[ order(row.names(theta)), ]
  theta$Lymphocyte <- theta$B + theta$CD4T + theta$CD8T + theta$NK
  return(theta)
}
```

```{r}
library(rstatix)
library(ggpubr)

id26TB <- All_sample_RNAseq %>% subset(Study %in% c("26TB") & timepoint=='D0') %>% select('LIMS_ID')
id27TB <- All_sample_RNAseq %>% subset(Study %in% c("27TB") & timepoint=='D0') %>% select('LIMS_ID')

theta1 <- get_theta(bp.res_ptb)
theta2 <- get_theta(bp.res_tbm)
theta2_1 <- theta2[id26TB$LIMS_ID,]
theta2_2 <- theta2[id27TB$LIMS_ID,]
theta3 <- get_theta(bp.res_healthy)


tmp1 <- pivot_longer(theta1,CD8T:Neutrophil)
tmp1$group <- rep('PTB',each=dim(tmp1)[1])
tmp2<- pivot_longer(theta2,CD8T:Neutrophil)
tmp2$group <- rep('TBM',each=dim(tmp2)[1])

tmp2_1<- pivot_longer(theta2_1,CD8T:Neutrophil)
tmp2_1$group <- rep('TBM (HIV+)',each=dim(tmp2_1)[1])
tmp2_2<- pivot_longer(theta2_2,CD8T:Neutrophil)
tmp2_2$group <- rep('TBM (HIV-)',each=dim(tmp2_2)[1])

tmp3 <- pivot_longer(theta3,CD8T:Neutrophil)
tmp3$group <- rep('Healthy',each=dim(tmp3)[1])
tmp<-rbind(tmp1,tmp2_1,tmp2_2,tmp3)

stat.test <- tmp %>%
  group_by(name) %>% 
  t_test(value ~ group) %>% 
  add_significance("p") %>%
  add_xy_position(x = "name")
stat.test


p <- ggplot(data=tmp,
       aes(x=name,
           y=value,
           color=factor(group, level = c('Healthy','PTB','TBM (HIV+)','TBM (HIV-)'))))+
  geom_boxplot() +
  geom_point(position=position_jitterdodge(jitter.width =0.3,jitter.height =0),
             alpha=0.1)+
  scale_color_manual(values=c("#A3BE8C","#81A1C1","#B48EAD","#D08770"))+
  labs(color='Group')+ 
  xlab('Cell type')+
  ylab('% Cell population')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold"))+
  stat_compare_means(
    method= "wilcox.test",
    aes(label = after_stat(p.signif)),
                     tip.length = 0.1,
                     bracket.size = 0.3,
                     step.increase = 0.5,
                     position=position_jitter(width = 0, height = 0.5),
    )
  # stat_pvalue_manual(stat.test, label = 'p.signif', 
  #                    tip.length = 0.01,
  #                    step.increase = 0,
  #                    vjust=0,
  #                    size=3.88, 
  #                    #y.position = c(0.9, 1, 0.9),
  #                    bracket.shorten = 0)
p

tmp %>% summarise(wilcox.p = wilcox.test(value ~ group, exact = FALSE))

tmp %>% 
  group_by(gene.name) %>% 
  summarise(p=wilcox.test(value~group)$p.value)

table(tmp$group)

tmp %>% group_by(name) %>% summarise(p=wilcox.test(value,group))


wilcox.test(filter(tmp, group=='PTB' & name=='Neutrophil')$value, 
            filter(tmp, group=='TBM (HIV+)' & name=='Neutrophil')$value, paired=FALSE)
pairwise.wilcox.test(Ozone, Month)


attach(airquality)
Month <- factor(Month, labels = month.abb[5:9])
## These give warnings because of ties :
pairwise.wilcox.test(tmp$name.tmp$group)
pairwise.wilcox.test(Ozone, Month, p.adjust.method = "bonf")
detach()

pairwise.wilcox.test(tmp$value,tmp$group)



tmp %>% stat_compare_means(method= "wilcox.test")
    
aes(label = after_stat(p.signif)),
                     tip.length = 0.1,
                     bracket.size = 0.3,
                     step.increase = 0.5,
    position=position_dodge(0.9)
```

#### 3.4.2.2. CNIH4 Expression Estimation

```{r}
get_z_vst <- function(bp,gene) {
  z <- get.exp(bp=bp, state.or.type="type")
  tmp <- vst(round(t(z[,,'Neutrophil'])),
             blind=T,
             nsub=dim(z[,,'Neutrophil'])[1],
             fitType='mean') %>% t() %>% as.data.frame()
  df <- data.frame(Neutrophil = tmp[,gene])
  cell_list <- c('CD8T', 'Monocyte','CD4T', 'B', 'NK', 'Neutrophil')
  
  for(i in 1:length(cell_list)){
    c <- cell_list[i]
    print(c)
    tmp <- vst(round(t(z[,,c])),blind=T,nsub=dim(z[,,'Neutrophil'])[1]) %>% t() %>% as.data.frame()
    df[,c] <- tmp[,gene]
  }
  return(df)
}

zptb_cnih4 <- get_z_vst(bp.res_ptb,'CNIH4')
ztbm_cnih4 <- get_z_vst(bp.res_tbm,'CNIH4')
zh_cnih4 <- get_z_vst(bp.res_healthy,'CNIH4')
```

```{r}

tmp1 <- pivot_longer(zptb_cnih4,Neutrophil:NK)
tmp1$group <- rep('PTB',each=dim(tmp1)[1])
tmp2<- pivot_longer(ztbm_cnih4,Neutrophil:NK)
tmp2$group <- rep('TBM',each=dim(tmp2)[1])
tmp3 <- pivot_longer(zh_cnih4,Neutrophil:NK)
tmp3$group <- rep('Healthy',each=dim(tmp3)[1])
tmp<-rbind(tmp1,tmp2,tmp3)

stat.test <- tmp %>%
  group_by(name) %>% 
  t_test(value ~ group) %>% 
  add_significance("p") %>%
  add_xy_position(x = "name")

p <- ggplot(data=tmp,
       aes(x=name,
           y=value,
           color=factor(group, level = c('Healthy','PTB','TBM'))))+
  geom_boxplot() +
  geom_point(position=position_jitterdodge(jitter.width =0.3),
             alpha=0.1)+
  scale_color_manual(values=c("#81A1C1","#B48EAD","#A3BE8C"))+
  labs(color='Group')+ 
  xlab('Cell type')+
  ylab('CNIH4 Z Estimation')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold"))+
  stat_pvalue_manual(stat.test, label = 'p.signif', tip.length = 0)
```

#### 3.4.2.3. PD-L1 Expression Estimation

```{r}
z <- get.exp(bp=bp.res_ptb, state.or.type="type")
tmp <- vst(round(t(z[,,'Neutrophil'])),
           blind=T,
           nsub=dim(z[,,'Neutrophil'])[1],
           fitType='mean') %>% t() %>% as.data.frame()
df <- data.frame(Neutrophil = tmp[,'CD274'])
```

```{r}
zptb_cd274 <- get_z_vst(bp.res_ptb,'CD274')
ztbm_cd274 <- get_z_vst(bp.res_tbm,'CD274')
zh_cd274 <- get_z_vst(bp.res_healthy,'CD274')
```

```{r}

tmp1 <- pivot_longer(zptb_cd274,Neutrophil:NK)
tmp1$group <- rep('PTB',each=dim(tmp1)[1])
tmp2<- pivot_longer(ztbm_cnih4,Neutrophil:NK)
tmp2$group <- rep('TBM',each=dim(tmp2)[1])
tmp3 <- pivot_longer(zh_cnih4,Neutrophil:NK)
tmp3$group <- rep('Healthy',each=dim(tmp3)[1])
tmp<-rbind(tmp1,tmp2,tmp3)

stat.test <- tmp %>%
  group_by(name) %>% 
  t_test(value ~ group) %>% 
  add_significance("p") %>%
  add_xy_position(x = "name")

p <- ggplot(data=tmp,
       aes(x=name,
           y=value,
           color=factor(group, level = c('Healthy','PTB','TBM'))))+
  geom_boxplot() +
  geom_point(position=position_jitterdodge(jitter.width =0.3),
             alpha=0.1)+
  scale_color_manual(values=c("#81A1C1","#B48EAD","#A3BE8C"))+
  labs(color='Group')+ 
  xlab('Cell type')+
  ylab('CNIH4 Z Estimation')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold"))+
  stat_pvalue_manual(stat.test, label = 'p.signif', tip.length = 0)
```

#### 3.4.2.4. ssGSEA for group + celltype

```{r}
library(GSVA)
library(BiocParallel)
library(ReactomeContentService4R)
library(msigdbr)
library(ggpmisc)

get_genelist_pathway_kegg <- function(hsa_ID){
  library("KEGGREST")
  names <- keggGet(hsa_ID)[[1]]$GENE
  namesodd <-  names[seq(0,length(names),2)]
  namestrue <- gsub("\\;.*","",namesodd)
}

#T cell receptor signaling pathway - Homo sapiens (human)
TCR_signaling<-get_genelist_pathway_kegg(hsa_ID = "hsa04660")

get_ssgsea <- function(bp.res){
  num_samples <- dim(bp.res@prism@mixture)[1]
  TCR_signaling_df <- data.frame()
  TCR_signaling_df[1:num_samples,]=NA
  for (i in 1:6){
  cellname = bp.res@prism@map[[i]] #"Neutrophil"
  z <- get.exp(bp=bp.res,
               state.or.type="type",
               cell.name = cellname
               )
  GSVA_targeted <- gsva(t(z), gset.idx.list=list(TCR_signaling=TCR_signaling),method="ssgsea",mx.diff=T)
  GSVA_targeted<-as.data.frame(t(GSVA_targeted))
  TCR_signaling_df[,cellname] = GSVA_targeted$TCR_signaling
  }
  rownames(TCR_signaling_df) <- rownames(GSVA_targeted)
  TCR_signaling_df <- TCR_signaling_df[,c('B','CD4T','CD8T','NK','Neutrophil','Monocyte')]
  return(TCR_signaling_df)
}


TCRsig_df_ptb <- get_ssgsea(bp.res = bp.res_ptb)
TCRsig_df_healthy <- get_ssgsea(bp.res = bp.res_healthy)
TCRsig_df_tbm <- get_ssgsea(bp.res = bp.res_tbm)

TCRsig_df_long_ptb <- pivot_longer(TCRsig_df_ptb,B:Monocyte)
TCRsig_df_long_healthy <- pivot_longer(TCRsig_df_healthy,B:Monocyte)
TCRsig_df_long_tbm <- pivot_longer(TCRsig_df_tbm,B:Monocyte)

TCRsig_df_long_ptb$group <- rep('PTB',each=dim(TCRsig_df_long_ptb)[1])
TCRsig_df_long_healthy$group <- rep('Healthy',each=dim(TCRsig_df_long_healthy)[1])
TCRsig_df_long_tbm$group <- rep('TBM',each=dim(TCRsig_df_long_tbm)[1])

tmp<-rbind(TCRsig_df_long_healthy,TCRsig_df_long_ptb,TCRsig_df_long_tbm)

stat.test <- tmp %>%
  group_by(name) %>% 
  t_test(value ~ group) %>% 
  add_significance("p") %>%
  add_xy_position(x = "name")
stat.test

p <- ggplot(data=tmp,
       aes(x=name,
           y=value,
           color=factor(group, level = c('Healthy','PTB','TBM'))))+
  geom_boxplot() +
  #scale_y_continuous( log_trans())+
  geom_point(position=position_jitterdodge(jitter.width =0.3,jitter.height =0),
             alpha=0.1)+
  scale_color_manual(values=c("#A3BE8C","#81A1C1","#B48EAD"))+
  labs(color='Group')+ 
  xlab('Cell type')+
  ylab('Enrichment score of T-cell receptor signaling pathways')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold"))+
  stat_pvalue_manual(stat.test, label = 'p.signif', tip.length = 0)
  # stat_compare_means(
  #   method= "wilcox.test",
  #   aes(label = after_stat(p.signif)),
  #                    tip.length = 0.1,
  #                    bracket.size = 0.3,
  #                    step.increase = 0.5,
  #                    position=position_jitter(width = 0, height = 0.5),
  #   )

p
p <- ggplot(data=TCR_signaling_df_long,aes(x=name,
                                           y=value,
                                           color=factor(name)))+
  geom_boxplot() +
  geom_point(position=position_jitterdodge(jitter.width =1.5,jitter.height =0),
             alpha=0.1)+
  scale_color_manual(values=c("#A3BE8C","#81A1C1","#88C0D0","#B48EAD","#D08770","#BF616A"))+
  labs(color='Group')+ 
  xlab('Cell type')+
  ylab('Enrichment score of T-cell receptor signaling pathways')+
  theme_bw()+
  theme(plot.title = element_text(size = 25),
        legend.position = "right",
        legend.text = element_text(size = 20) ,
        legend.title  = element_text(size = 20,color="black",face="bold"),
        axis.text = element_text(size = 25),
        axis.text.x=element_text(color="black",size=13,face="bold",angle = 45,vjust = 1, hjust=1),
        axis.title.x = element_text(size = 20,color="black",face="bold"),
        axis.text.y=element_text(color="black",size=20),
        axis.title.y = element_text(size = 20,color="black",face="bold"),
        axis.title= element_text(size = 40,color="black",face="bold"))
  # stat_pvalue_manual(stat.test, label = 'p.signif', 
  #                    tip.length = 0.01,
  #                    step.increase = 0,
  #                    vjust=0,
  #                    size=3.88, 
  #                    #y.position = c(0.9, 1, 0.9),
  #                    bracket.shorten = 0)
p
```

### 3.5. DESEQ2 Analysis

```{r}
library(EnhancedVolcano)
library(comprehenr)

df <- filter(vst_ptb_tbm,Type=='PTB') %>% select(c('LIMS_ID','CNIH4level'))
PTB_sample_RNAseq <- All_sample_RNAseq %>% subset(Study %in% c("28TB","29TB"))
count_data <-count_all[,rownames(PTB_sample_RNAseq)]
count_data<-count_data[ , !(names(count_data) %in% c('HOA7818A92'))] # drop 1 patients not in vst

df<- df[order(df$LIMS_ID),] #col
df$CNIH4level<-factor(df$CNIH4level,levels=c(1,2))
df$LIMS_ID<-NULL

count_data<-count_data[ , order(names(count_data))]
anno_symbol <- anno[,c("gene_id", "gene_symbol")] %>% filter(gene_id %in% rownames(count_data))
rownames(anno_symbol) <- anno_symbol$gene_id
anno_symbol <- anno_symbol[rownames(count_data),]
count_data <- cbind(genenames=anno_symbol$gene_symbol,count_data)
count_data <-count_data %>% filter(genenames %in% names(RNA_data) & genenames!='CNIH4')

count_data$genenames<-NULL
anno_symbol <- anno[,c("gene_id", "gene_symbol")] %>% filter(gene_id %in% rownames(count_data))

dup_genes_id <- anno_symbol[duplicated(anno_symbol$gene_symbol), ]$gene_id
count_data <- count_data[!(rownames(count_data) %in% dup_genes_id),]

dds <- DESeqDataSetFromMatrix(count_data, colData=df, ~CNIH4level)
dds <- DESeq(dds)

#results(dds, contrast=c("condition","C","B")) meaning genes with:
#logFC > 0 are overexpressed in C and underexpressed in B.
#logFC < 0 means underexpressed in C and overexpressed in B

res1 <- results(dds,contrast=c('CNIH4level',2,1),alpha=0.05)
#res2 <- lfcShrink(dds, coef= 'CNIH4level_2_vs_1', type="apeglm")
summary(res1)

labels <- mapvalues(rownames(res1), 
          from=anno_symbol$gene_id, 
          to=anno_symbol$gene_symbol)

EnhancedVolcano(res1,
    lab = labels,
    x = 'log2FoldChange',labSize = 2.0,
    pCutoff = 0.05,
    FCcutoff = log2(1.5),
    y = 'padj',)

get_DEGgenes <- function(df,reg){
    if(reg=='high'){
      key <- intersect(rownames(df)[which(df$log2FoldChange>=log2(1.5))], rownames(df)[which(df$padj<0.05)])
    }
    if(reg=='low'){
      key <- intersect(rownames(df)[which(df$log2FoldChange<=-log2(1.5))], rownames(df)[which(df$padj<0.05)])
    }
    results <- as.data.frame((df)[which(rownames(df) %in% key),])
    return(results)
}

deg_high <- rownames(get_DEGgenes(as.data.frame(res1),reg='high'))
deg_low <- rownames(get_DEGgenes(as.data.frame(res1),reg='low'))

deg_high <- to_vec(for(i in 1:length(deg_high)) filter(anno_symbol,gene_id==deg_high[i])$gene_symbol)
deg_low <- to_vec(for(i in 1:length(deg_low)) filter(anno_symbol,gene_id==deg_low[i])$gene_symbol)
```

### 3.6. Pathway Analysis

```{r}
ORA_bar_plot <- function(df,name,n=5){
  n <- min(nrow(df),n)
  df <- df[1:n,]
  #n_break <- as.integer(max(df$log_pvalue))
  p <- ggplot(aes(x= ID,y = log_pvalue),data =df) + 
  geom_col(position = "stack", 
           alpha = 0.5,fill="#4292c6") +
  geom_text(aes(x=ID,y=0.1,label =ID), 
            size=3,fontface='bold',hjust=0)+
  ggtitle(name)+
  #geom_text(aes(x=ID,y=pos,label =log_pvalue), hjust=0.5) +
  #scale_y_continuous(breaks = 1:n_break)+ 
  coord_flip()+
  labs(x="", y="Log10 P value") +
  #scale_fill_manual(values=c("#4292c6")) +
  theme_bw()+
  theme(plot.title = element_text(size = 20),
        legend.text = element_text(size = 15) ,
        legend.position="right",
        legend.title = element_text(size = 13,color="black",face="bold"),
        axis.text.x=element_text(color="black",size=13),
        axis.title.x = element_text(size = 13,color="black",face="bold"),
        axis.text.y=element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_text(size = 13,color="black",face="bold"))
  
  #p
  return(p)
}
```

```{r}
library(msigdbr)
library(dplyr)
library(clusterProfiler)
# db <- msigdbr(species = "Homo sapiens", category = "H") %>%
#   dplyr::select(gs_name, human_gene_symbol)
#C5, C8

# db <- msigdbr(species = "Homo sapiens", category = "C5") %>%
#   filter(gs_subcat=="GO:BP") %>% #C5
#   dplyr::select(gs_name, human_gene_symbol)

db <- msigdbr(species = "Homo sapiens", category = "C8") %>%
  dplyr::select(gs_name, human_gene_symbol)

dim(db)

ORA_analysis <- function(gene_list){
  temp <- enricher(gene_list, TERM2GENE=db, pvalueCutoff = 1, qvalueCutoff = 1)
  temp <- temp@result
  if(!is.na(table(temp$p.adjust < padj)["TRUE"]) &  table(temp$p.adjust < padj)["TRUE"]>10){
    temp <- temp %>% filter(p.adjust<padj) %>%
    dplyr::arrange(pvalue)
    } 
  else{
    temp <- temp %>%
    dplyr::arrange(pvalue)
    temp <- temp[1:min(nrow(temp),10),]
    }
  # df <- temp %>%
  # dplyr::arrange(pvalue) %>%
  # dplyr::mutate(log_pvalue=-log10(pvalue),
  #               pos = ifelse(log_pvalue <4,log_pvalue + 1,log_pvalue + 0.5))
  # ORA_bar_plot(df)
  return(temp)
}

ora_low <- ORA_analysis(deg_low)
df1 <- ora_low %>%
  dplyr::arrange(pvalue) %>%
  dplyr::mutate(log_pvalue=-log10(pvalue),
                pos = ifelse(log_pvalue <4,log_pvalue + 1,log_pvalue + 0.5))
p1<-ORA_bar_plot(df1,'Genes down-regulated in high CNIH4')
p1
ora_high <- ORA_analysis(deg_high)
df2 <- ora_high %>%
  dplyr::arrange(pvalue) %>%
  dplyr::mutate(log_pvalue=-log10(pvalue),
                pos = ifelse(log_pvalue <4,log_pvalue + 1,log_pvalue + 0.5))
p2<-ORA_bar_plot(df1,'Genes up-regulated in high CNIH4')


n = 5
df1 <- df1[1:min(nrow(df1),n),] %>% mutate(group='downregulated genes') %>% arrange(ID)
df2 <- df2[1:min(nrow(df2),n),] %>% mutate(group='upregulated genes') %>% arrange(ID)
df <- rbind(df1,df2)
df$ID <- factor(df$ID, levels = df$ID)

#n_break <- as.integer(max(df$log_pvalue))
p <- ggplot(data =df,aes(x= ID,y = log_pvalue,fill=group)) + 
  geom_col(position = 'stack',
         alpha = 0.5,
         aes(x=ID,y = log_pvalue,
             fill = group)) +
scale_fill_manual( values = c('#5E81AC','#BF616A'))+
geom_text(aes(x=ID,y=0.1,label =ID), 
          size=3,fontface='bold',hjust=0)+
#geom_text(aes(x=ID,y=pos,label =log_pvalue), hjust=0.5) +
#scale_y_continuous(breaks = 1:n_break)+ 
coord_flip()+
labs(x="", y="Log10 P value") +
#scale_fill_manual(values=c("#4292c6")) +
theme_bw()+
theme(plot.title = element_text(size = 20),
      legend.text = element_text(size = 15) ,
      legend.position="right",
      legend.title = element_text(size = 13,color="black",face="bold"),
      axis.text.x=element_text(color="black",size=13),
      axis.title.x = element_text(size = 13,color="black",face="bold"),
      axis.text.y=element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_text(size = 13,color="black",face="bold"))
p
```

### 3.7. Isoforms Correlation Analysis

```{r}
write.csv(salmons12,'ptb_CNIH4_CD274_salmon_vst.csv',row.names = TRUE)
```

```{r}
salmons <- read.csv(paste0(path_input,'/Data/ptb_CNIH4_CD274_salmon_counts.csv'))

salmons12 <- salmons %>% filter(Run=='1+2') %>% tibble::column_to_rownames('transcript_name') %>% select(colnames(salmons)[8:dim(salmons)[2]]) %>% t()

salmons12 <- as.data.frame(vst(round(salmons12),blind=T, nsub=295))
salmons12 <- merge(salmons12,vst_data,by=0) %>% select(c(colnames(salmons12),'CT_mean'))

```

```{r}
library(grid)
a <- ifelse(colnames(salmons12) %in% c('CNIH4-201','CNIH4-202','CNIH4-203','CNIH4-205', 'CD274-201','CD274-202'), "red", "black")
p01$gtable$grobs[[5]]$gp=gpar(col=a)
p01
```

```{r}
cor_method = 'pearson'
mat <- cor(salmons12,
                      use='pairwise.complete.obs',
                      method = cor_method)

p.mat <- cor.pval.test(salmons12, 
                                  salmons12, 
                                  method=cor_method, 
                                  use='pairwise.complete.obs')

#col=c("#001164", 'white', "#FF681E")
#col=c("#5E81AC", '#EBCB8B', "#BF616A")
col=c("#395b85", 'white', "#FF681E")
# CNIH4 vs 25 ICs
mat1 <- mat
p.mat1 <- p.mat
labels1 <-round(mat1,2)
vals1 <- labels1
vals1[p.mat1 > 0.05] <- 0
labels1[p.mat1 > 0.05] <- ''

myBreaks <- c(seq(-1, 0, length.out=ceiling(1000/2) + 1),
              seq(1/1000, 1, length.out=floor(1000/2)))

p01 <- pheatmap(vals1,
               color = colorRampPalette(col)(1000),
               breaks=myBreaks,
               display_numbers=labels1,
               show_colnames = F,legend = F)
p01
row.order <- p01$tree_row$order
col.order <- p01$tree_col$order
p1 <- as.ggplot(p01)
```

### 3.8. AUC

```{r}
ptb_ct40 <- vst_data %>% select(c('LIMS_ID','CNIH4','CT_mean')) %>% filter(CT_mean==40)
tbm_ct40 <- Data_26_27_CT %>% mutate(CT_mean=NAT) %>% select(c('LIMS_ID','CNIH4','CT_mean')) %>% filter(CT_mean==40)
row.names(tbm_ct40) <- tbm_ct40$LIMS_ID
ptb_tbm_ct40 <- rbind(ptb_ct40,tbm_ct40)


healthy <- healthy_df %>% select(c('LIMS_ID','CNIH4'))
write.csv(ptb_tbm_ct40,'ptb_tbm_ct40_CNIH4.csv',row.names = FALSE)
write.csv(healthy,'healthy_CNIH4.csv',row.names = FALSE)
```

# Draft

```{r}
colnames(salmon12)
```
